### 2016-09-21 Documentation/paper/paper.tex
Adding WIP writeup.

\documentclass[twocolumn]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\section{Background}\label{background}

\subsection{Usage}\label{usage}

This system was originally designed for use at the Spallation Neutron
Source at Oak Ridge National Laboratory, then subsequently at the ISIS
neutron source of the Science and Technology Facilities Council. These
facilities operate pulsed neutron sources for scientific and industrial
research, with many independent instruments receiving neutrons from a
source for use in experiments.

In both cases autoreduction was intended to serve as part of an
automation system to handle data produced by these neutron beam
instruments. However, the process is applicable to beamline instruments
in general, such as might be used on muon or X-ray beams.

\subsection{Data reduction}\label{data-reduction}

The autoreduction service exists to reduce beamline instrument data. An
instrument produces discrete tranches of data, referred to as `runs', in
service of experiments. This raw data typically needs to be processed --
`reduced' -- before it can be used by scientists, by running a script on
it. Although the script itself need not change often, it may have
configurable parameters -- variables -- which ought to be changed
frequently.

The autoreduction system is intended to automate this process.
Instrument scientists provide it with reduction scripts - in a specified
location on a shared file archive - and sets of variables to use to
reduce runs. The system watches for the completion of runs, and runs the
appropriate script, with the correct variables, on them, supplying the
reduced data to an archive for users to retrieve.

\subsection{Requirements}\label{requirements}

The system is intended primarily to serve the instrument scientists --
who manage beamline instruments -- and users who use the instruments to
run experiments. The key requirements for these users were to

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Automate the reduction of data from beam instruments, using scripts
  provided by instrument scientists.
\item
  Show the status of reduction on runs, as well as the results and
  locations of reduced data, to users.
\item
  Allow instrument scientists to set the parameters used for reduction,
  in advance and retroactively.
\item
  Allow users and instrument scientists to see what script, with which
  parameters, was used to reduce a run.
\item
  Allow users and instrument scientists to modify the parameters used
  for a run, and re-run reduction using new parameters or scripts.
\end{enumerate}

Additional constraints were to

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Limit access to the system to ensure that only staff and scientists
  can access runs and instruments.
\item
  Utilise existing authentication systems to validate identities and
  permissions for (1).
\item
  Allow scalability for processing large amounts of data in a timely
  manner.
\item
  Integrate with ICAT -- the scientific metadata catalogue in use at
  ISIS.
\end{enumerate}

\section{System architecture}\label{system-architecture}

The architecture is based on a queue node, which co-ordinates
communication between all components of the system. This maintains
separate message queues, which allow components to act on messages from
other components and update the system. These components are

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  Workers for reduction processing
\end{enumerate}

When the listener detects that a new job should be created, it sends a
request to do so to \emph{Data Ready}. The state database consumes the
request and creates the corresponding job in the database, before
sending a request to process it to \emph{Reduction Pending}. A reduction
worker takes this message and runs the appropriate script, sending the
result to either \emph{Reduction Complete} or \emph{Reduction Error},
where it's consumed by the state database to update the status of the
run.

\subsection{Message queue}\label{message-queue}

Apache ActiveMQ is used as the message queueing system, with message
contents as JSON-formatted objects. The intention of the message is
conveyed by which queue it's placed in, rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature, which allows a message to be delivered a given
time after it's been pushed to the queue.

Messages contain metadata for the run such as a (unique) run number and
version, the experiment and instrument that the data is associated with,
and any logs or errors resulting from reduction. They also carry the
necessary information to carry out the data reduction - the Python
script to run on the data, paths to the data, and variables to be used
by the script.

Data files typically run in the hundreds of MB at least, so would be
impractical to send directly in a message; they're provided as file
paths on a shared file archive. Meanwhile, the reduction script to be
used is sent as a string; the script is served from the state database,
and using the message queue directly to send it obviates the need to
rely on a potentially flaky shared file store within the system.

\subsection{Job listener}\label{job-listener}

When a new run has been completed on the beam line, the data files are
placed in a shared filesystem. A node runs a Python watchdog daemon that
tracks changes in this filesystem, and when a new run is added, sends a
message to \emph{Data Ready} with details of the run. This particular
choice of listener isn't crucial; anything would work as long as it
pushed the same message to the queue. In the current production system
at ISIS, this is the same node as the state database itself.

\subsection{State database}\label{state-database}

A node keeps track of the status of runs in a local SQL database. This
server hosts a Python service responsible for listening on \emph{Data
Ready}, to create new runs and then dispatch them to \emph{Reduction
Pending}. It manages variables for reduction, and selects the correct
set for the run. The same server is responsible for serving the
Python/Django web app. The database is therefore accessed through
Django's object interface, and reduction runs, etc., are tracked as
Django objects.

The daemon receives status updates from reduction workers on
\emph{Reduction Started}, \emph{Reduction Complete} and \emph{Reduction
Error}, making the appropriate changes to the database. On some messages
in the error queue, the daemon will create and schedule the appropriate
retry runs. A system for emailing notifications of run failures to
administrators is also implemented here.

\subsection{Reduction worker}\label{reduction-worker}

The data reduction itself is performed by a worker node, running a
Python daemon listening on \emph{Reduction Pending}. When the worker
consumes a message, it will spawn a process starting the job and
notifying \emph{Reduction Started}. This process tests for access to the
filesystems used for storing the raw and reduced data, triggering a
scheduled retry later -- on \emph{Reduction Error} -- if they're
unavailable. Otherwise, it will proceed with the reduction, loading and
then running the provided script.

On a successful run, the job will notify \emph{Reduction Completed} with
the location of the reduced data; otherwise, it will send the reason for
failure to \emph{Reduction Error}, most likely without triggering a
retry. In both cases it will send logs of the process, and clean up
after itself. Some runs associated with the same experiment would write
output to the same directory; to prevent clashes due to this, the node
contains an internal queue holding all runs associated with an
experiment for as long as it's actively reducing another run for the
same experiment.

\section{Interface}\label{interface}

\subsection{Reduction scripts}\label{reduction-scripts}

The wholly automated portion of the system revolves around running
scientist-provided scripts to reduce raw instrument data. These scripts
are provided as Python scripts on a per-instrument basis, typically
using the Mantid software package to do the heavy lifting. They're
stored on a shared file store in a known location, where they can be
modified at will by instrument scientists; runs store the script they
were reduced by in the system database, but new runs will be reduced
using the current script on the file store.

Aside from overall logic, these scripts typically require parameters
such as calibration files, information about how the instrument was run,
output settings, and so on. While some users prefer to hard-code these
in their scripts, others would rather make use of a system for managing
these variables separate from the script itself. A list of variables and
default values is provided in a Python file similar to the reduction
script, but the autoreduction system keeps track of variable
configurations provided to it through the web app, and applies them to
the relevant runs.

The reduction scripts need to integrate with the automation system, and
as such must conform to a certain specification: the script must have a
\emph{main()} method, taking an input file and an output directory as
arguments. If the script uses system-supplied variables, it must have a
certain \emph{import} directive, which serves as a point of injection
for the variables when it is run.

Mantid provides a wrapper for data reduction through its Python
interface, and for many instruments the whole reduction processing is
also included. Writing reduction scripts for those instruments is
essentially trivial, boiling down to some boilerplate with very little
difference between instruments.

\subsection{Web app}\label{web-app}

The web app provides the user-facing interface for managing reduction.
It was developed in Python, using the Django web framework, and is
tightly integrated with the state database.

Users log in via the ISIS User Office -- using their federated
credentials -- and their level of access is then governed by ICAT's
information on the experiments and instruments they should be able to
see. A searchable index of runs is displayed on the front page, sorted
by instrument, experiment and run number, showing their reduction
status. Runs, experiments and instruments displayed here have links to
their summary pages.

Each run has its own summary page with detailed information; a user can
see the status of the reduction, where the reduced data is, and the
script and variables that were used to reduce it. From here the run can
be re-run, with or without modifying the variables used. Any
experimenter can access this page for their runs, and it's intended that
external scientists running experiments be able to control their data
reduction directly in this way.

Experiments also have summary pages, showing all the runs that are
associated with a given experiment along with their status and data
locations. Metadata about the experiment is retrieved from ICAT and
displayed here.

Instrument scientists can access a summary page for their instruments,
showing the current status of runs on an instrument, as well as current
and upcoming run variables. From here instrument scientists can assign
sets of variables by experiment and run number, which will then be used
automatically as appropriate for new runs. Batch re-running of past jobs
is also possible here. This is intended to be the main point of access
for instrument scientists to control data reduction.

Administrators can access everything above, and additionally have access
to pages displaying all queued and failed jobs. These pages provide an
overview of the status of the system at a glance, and have controls for
batch operations on failed jobs such as to re-run them.

\section{Current status}\label{current-status}

The system is deployed at ISIS, in limited use. The frontend node,
serving the message queue as well as managing the state and web app, is
a Windows Server system running on a Hyper-V cluster; it serves the web
app using Microsoft's Internet Information Services (IIS) and FastCGI.
There is one reduction node, running Red Hat Enterprise Linux on a
dedicated Dell PowerEdge R820 server -- reducing large amounts of data
is very CPU-intensive.

It is planned that the autoreduction system be developed to further meet
the needs and tastes of potential users at ISIS and other particle
facilities, and enter a more prominent role in automating data
processing there. Future development to this end may involve

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve adding more reduction workers, for example.
\item
  Integrating other methods of listening for new runs -- the current
  method of watching a file archive is specific to ISIS.
\item
  Improving portability and deployability of the current software; the
  state database/webapp in particular is currently unsupported for
  Linux, and the whole system is somewhat nontrivial to deploy even to a
  development environment.
\end{enumerate}

\end{document}

### 2016-09-21 Documentation/paper/paper.tex
Added some screenshots and citations.

@@
 \documentclass[twocolumn]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
 \usepackage[unicode=true]{hyperref}
 \hypersetup{
+            pdftitle={Autoreduction - an automated data reduction system for beam instruments},
+            pdfauthor={J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory - jrc91@cam.ac.uk},
             pdfborder={0 0 0},
             breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 
-\date{}
+\title{Autoreduction - an automated data reduction system for beam instruments}
+\author{J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory -
+jrc91@cam.ac.uk}
+\date{23/09/2015}
 
 \begin{document}
+\maketitle
+
+\subsection*{Abstract}\label{abstract}
+
+\section{Introduction}\label{introduction}
 
@@
 \begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
 \item
@@
 \item
-  Integrate with ICAT -- the scientific metadata catalogue in use at
-  ISIS.
+  Integrate with ICAT \cite{icat} -- the scientific metadata catalogue in use
+  at ISIS .
 \end{enumerate}
@@
 
+\begin{figure*}[!htbp]
+\includegraphics{system.png}
+\caption{How the autoreduction system fits into the ISIS workflow.}
+\end{figure*}
+
 \subsection{Message queue}\label{message-queue}
 
-Apache ActiveMQ is used as the message queueing system, with message
-contents as JSON-formatted objects. The intention of the message is
-conveyed by which queue it's placed in, rather than a field in the
+Apache ActiveMQ \cite{activemq} is used as the message queueing system, with
+message contents as JSON-formatted objects. The intention of the message
+is conveyed by which queue it's placed in, rather than a field in the
 message itself. Runs can be `scheduled' simply by using ActiveMQ's
@@
 
+\begin{figure*}
+\centering\includegraphics[width=0.8\linewidth]{index.png}
+\caption{The web app index, showing recent runs.}
+\end{figure*}
+
 Each run has its own summary page with detailed information; a user can
@@
 
+\section{Conclusion}\label{conclusion}
+
+\begin{thebibliography}{9}
+\bibitem{icat}
+    The ICAT Collaboration,
+    \emph{The Icat Project.},
+    2014,
+    \href{https://doi.org/10.5286/SOFTWARE/ICAT}{10.5286/SOFTWARE/ICAT}.
+
+\bibitem{activemq}
+    Apache Software Foundation,
+    \emph{Apache Activemq},
+    \url{http://http://activemq.apache.org/},
+\end{thebibliography}
 \end{document}

### 2016-09-22 Documentation/paper/paper.tex
Updating paper, removing unused files.

@@
 \documentclass[twocolumn]{article}
+
 \usepackage[unicode=true]{hyperref}
-\hypersetup{
-            pdftitle={Autoreduction - an automated data reduction system for beam instruments},
-            pdfauthor={J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory - jrc91@cam.ac.uk},
-            pdfborder={0 0 0},
-            breaklinks=true}
+\usepackage{enumitem}
 \usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
 
-\title{Autoreduction - an automated data reduction system for beam instruments}
-\author{J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory -
-jrc91@cam.ac.uk}
+\title{\textbf{Autoreduction - an automated data reduction system for beam instruments}}
+\author{J. R. Corderoy\\
+ISIS Facility, Rutherford Appleton Laboratory\\
+Email: jrc91@cam.ac.uk}
 \date{23/09/2015}
@@
 
+A key step for users of large research facilities is the routine
+processing of instrument data before use. Autoreduction is a software
+system designed to automate this process, integrated with other
+pre-existing facility systems and software packages, and provide
+an interface for users to control it.
+
 \section{Introduction}\label{introduction}
+
+High-energy particle facilities, such as the ISIS Neutron and Muon
+Facility, allow users in academic and industrial research
+to perform experiments using instruments set up to use high-energy
+particle beams. Common to most instruments is the need to process -- 
+`reduce' -- raw data collected from an instrument into a usable dataset.
+
+The goal for the autoreduction system is to provide a useful automation
+step in this process. It allows data coming off an instrument to be
+automatically reduced using a dedicated software package such as 
+Mantid\cite{mantid}, while lending transparency to the process and
+letting users control it through a straightforward web interface.
+
+Presented below is an overview of the motivation and design of the system,
+its use and interface, and its current status in production at ISIS.
 
@@
 
-\begin{enumerate}
+\begin{enumerate}[noitemsep]
 \item
@@
 
-\begin{enumerate}
+\begin{enumerate}[noitemsep,resume]
 \item
@@
 \item
-  Integrate with ICAT \cite{icat} -- the scientific metadata catalogue in use
-  at ISIS .
+  Integrate with ICAT\cite{icat} -- the scientific metadata catalogue in use
+  at ISIS.
 \end{enumerate}
@@
 
-\begin{enumerate}
+\begin{itemize}[noitemsep]
 \item
@@
   Workers for reduction processing
-\end{enumerate}
+\end{itemize}
 
@@
 
-\begin{figure*}[!htbp]
-\includegraphics{system.png}
+\begin{figure*}
+\centering\includegraphics[width=1.15\linewidth,angle=90,origin=c]{system.png}
 \caption{How the autoreduction system fits into the ISIS workflow.}
@@
 
-Apache ActiveMQ \cite{activemq} is used as the message queueing system, with
+Apache ActiveMQ\cite{activemq} is used as the message queueing system, with
 message contents as JSON-formatted objects. The intention of the message
@@
 set for the run. The same server is responsible for serving the
-Python/Django web app. The database is therefore accessed through
+Python/Django\cite{django} web app. The database is therefore accessed through
 Django's object interface, and reduction runs, etc., are tracked as
@@
 same experiment.
+
+\begin{figure*}
+\centering\includegraphics[width=0.8\linewidth]{index.png}
+\caption{The web app index, showing recent runs.}
+\end{figure*}
 
@@
 
-Users log in via the ISIS User Office -- using their federated
-credentials -- and their level of access is then governed by ICAT's
-information on the experiments and instruments they should be able to
-see. A searchable index of runs is displayed on the front page, sorted
+Users log in via the ISIS User Office system -- using credentials 
+granted for facility-wide use -- and their level of access is then 
+governed by ICAT's information on the experiments and instruments they 
+should be able to see. A searchable index of runs is displayed on the front page, sorted
 by instrument, experiment and run number, showing their reduction
@@
 their summary pages.
-
-\begin{figure*}
-\centering\includegraphics[width=0.8\linewidth]{index.png}
-\caption{The web app index, showing recent runs.}
-\end{figure*}
 
@@
 serving the message queue as well as managing the state and web app, is
-a Windows Server system running on a Hyper-V cluster; it serves the web
-app using Microsoft's Internet Information Services (IIS) and FastCGI.
-There is one reduction node, running Red Hat Enterprise Linux on a
-dedicated Dell PowerEdge R820 server -- reducing large amounts of data
-is very CPU-intensive.
+a Windows Server system running on a Hyper-V\cite{hyper-v} virtualisation
+cluster; it serves the web app using Microsoft's Internet Information
+Services (IIS)\cite{iis} and FastCGI\cite{fcgi}. There is one reduction node, 
+running Red Hat Enterprise Linux 7\cite{rhel} on a dedicated server -- 
+reducing large amounts of data is very CPU-intensive.
 
@@
 
-\begin{thebibliography}{9}
+The autoreduction system offers a convenient way of automating data reduction
+on beamline instruments. It uses a scalable architecture to allow prompt
+reduction of data from a large number of instruments, and utilises a web app
+frontend to allow users to control the reduction process manually and verify
+that the correct reduction was run.
+
+The system is currently in limited use at ISIS, with more instrument scientists
+interested in using it. The source code can be found on GitHub\cite{source}.
+
+\begin{thebibliography}{99}
+\bibitem{mantid}
+    O. Arnold, et al.,
+    \emph{Mantid -- Data analysis and visualization package for neutron scattering and $\mu$SR experiments},
+    Nuclear Instruments and Methods in Physics Research Section A, Volume 764, 11 November 2014, Pages 156-166,
+    \href{http://dx.doi.org/10.1016/j.nima.2014.07.029}{10.1016/j.nima.2014.07.029}.
+
 \bibitem{icat}
@@
     2014,
-    \href{https://doi.org/10.5286/SOFTWARE/ICAT}{10.5286/SOFTWARE/ICAT}.
+    \href{https://doi.org/10.5286/SOFTWARE/ICAT}{10.5286/software/icat}.
 
@@
     \emph{Apache Activemq},
-    \url{http://http://activemq.apache.org/},
+    \url{http://activemq.apache.org/}.
+
+\bibitem{django}
+    Django Software Foundation,
+    \emph{Django},
+    \url{https://www.djangoproject.com/}.
+
+\bibitem{hyper-v}
+    Microsoft Corporation,
+    \emph{Hyper-V},
+    \url{https://technet.microsoft.com/en-us/library/mt169373.aspx}.
+
+\bibitem{iis}
+    Microsoft Corporation,
+    \emph{IIS},
+    \url{http://www.iis.net/}.
+
+\bibitem{fcgi}
+    \emph{FastCGI},
+    \url{https://github.com/FastCGI-Archives/FastCGI.com}.
+
+\bibitem{rhel}
+    Red Hat, Inc,
+    \emph{Red Hat Enterprise Linux},
+    \url{https://www.redhat.com/en/technologies/linux-platforms/enterprise-linux}.
+
+\bibitem{source}
+    \emph{Autoreduction repository},
+    \url{https://github.com/mantidproject/autoreduce}.
+
 \end{thebibliography}

### 2016-09-22 ISISendOfRunMonitor.py
Fixing monitor log location.

@@ -9,7 +9,7 @@ INST_FOLDER = r"\\isis\inst$\NDX%s\Instrument"
 DATA_LOC = r"\data\cycle_%s\\"
 SUMMARY_LOC = r"\logs\journal\SUMMARY.txt"
 LAST_RUN_LOC = r"\logs\lastrun.txt"
-LOG_FILE = r"xx\monitor_log.txt"
+LOG_FILE = r"monitor_log.txt"
 INSTRUMENTS = [{'name': 'LET', 'use_nexus': True},
                {'name': 'MERLIN', 'use_nexus': False},
                {'name': 'MAPS', 'use_nexus': True},

### 2016-09-22 Documentation/paper/paper.tex
Fixing architecture wrt queue.

@@
 \item
-  Workers for reduction processing
+  A worker for reduction processing
 \end{itemize}
@@
 request and creates the corresponding job in the database, before
-sending a request to process it to \emph{Reduction Pending}. A reduction
+sending a request to process it to \emph{Reduction Pending}. The reduction
 worker takes this message and runs the appropriate script, sending the
@@
 \centering\includegraphics[width=1.15\linewidth,angle=90,origin=c]{system.png}
-\caption{How the autoreduction system fits into the ISIS workflow.}
+\caption{How the current autoreduction system fits into the ISIS workflow.}
 \end{figure*}
@@
 
-The system is deployed at ISIS, in limited use. The frontend node,
-serving the message queue as well as managing the state and web app, is
-a Windows Server system running on a Hyper-V\cite{hyper-v} virtualisation
-cluster; it serves the web app using Microsoft's Internet Information
-Services (IIS)\cite{iis} and FastCGI\cite{fcgi}. There is one reduction node, 
-running Red Hat Enterprise Linux 7\cite{rhel} on a dedicated server -- 
-reducing large amounts of data is very CPU-intensive.
+The system is deployed at ISIS, in limited use. The frontend node, managing
+the state and web app, is a Windows Server system running on a 
+Hyper-V\cite{hyper-v} virtualisation cluster; it serves the web app using
+Microsoft's Internet Information Services (IIS)\cite{iis} and 
+FastCGI\cite{fcgi}.
+
+There is one reduction node, running Red Hat Enterprise Linux 7\cite{rhel}
+on a dedicated server -- reducing large amounts of data is very CPU-intensive.
+This node also serves the message queue; subsequent worker nodes would
+not have multiple message queues, and it would be wise to separate the
+message queue from the worker entirely in this case.
 
@@
   Expanding the system to accommodate greater volume of use -- this
-  might involve adding more reduction workers, for example.
+  might involve accomodating more reduction workers, for example.
 \item

### 2016-10-21 Documentation/paper/paper.tex
Updating paper and system diagram

@@
 
-\title{\textbf{Autoreduction - an automated data reduction system for beam instruments}}
-\author{J. R. Corderoy\\
+\title{\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}}
+\author{J. R. Corderoy, L. Greenwood, M. Noble, D. Oram and A. J. Markvardsen (code contributors)\\
 ISIS Facility, Rutherford Appleton Laboratory\\
-Email: jrc91@cam.ac.uk}
+Email: someone with an STFC email account}
 \date{23/09/2015}
@@
 
-A key step for users of large research facilities is the routine
+A key step for users of large research facilities is the
 processing of instrument data before use. Autoreduction is a software
@@
 
+This article describes the system setup for Autoreduction at the ISIS Facility;
+it motivation and design, its use and interface, and its current status in production at ISIS.
+
 \section{Introduction}\label{introduction}
 
-High-energy particle facilities, such as the ISIS Neutron and Muon
+Large scale research facilities, such as the ISIS Neutron and Muon
 Facility, allow users in academic and industrial research
-to perform experiments using instruments set up to use high-energy
-particle beams. Common to most instruments is the need to process -- 
-`reduce' -- raw data collected from an instrument into a usable dataset.
+to perform experiments using instruments set up to probe the inner 
+structure and dynamics of materials. 
+Common to most instruments is the need to process -- 
+`reduce' -- raw data collected from an instrument into a form
+that a user can interprete or can do further analysis on. For example
+by removing instrument specific artifacts from the measured data, 
+transforming the data into different units and/or
+into data formats readably by further analysis software.
 
-The goal for the autoreduction system is to provide a useful automation
-step in this process. It allows data coming off an instrument to be
-automatically reduced using a dedicated software package such as 
-Mantid\cite{mantid}, while lending transparency to the process and
+The purpose of the autoreduction system is to provide a useful automation
+step in this process. The system described in this works allows data coming 
+off an instrument to be automatically reduced using a dedicated software package 
+such as Mantid\cite{mantid}, while lending transparency to the process and
 letting users control it through a straightforward web interface.
 
-Presented below is an overview of the motivation and design of the system,
-its use and interface, and its current status in production at ISIS.
+TO DO: some reference that automation of data reduction also persued at
+other large scale facilities: Anders writing from NOBUGS conference: such as 
+possibly mention Diamand has a batch script based system 
+for macromolecular beamlines (talk by Dr Markus Gerstel, Diamond). Dr Martin Rehr 
+mentioned in his talk on "Image data Management System" that auto processing was
+used. Dr Sergey Stepanov talk "Integration of fast detectors into.... macromolecular
+crystallography beamlines at the Advanced Photon Source" used auto processing - seemed
+to be a theme for MX beamlines.
 
@@
 
-\subsection{Usage}\label{usage}
+The autoreduction system at ISIS was inspired by an autoreduction setup at the
+the Spallation Neutron Source (SNS) at Oak Ridge National Laboratory \cite{autoreductionSNS}.
 
-This system was originally designed for use at the Spallation Neutron
-Source at Oak Ridge National Laboratory, then subsequently at the ISIS
-neutron source of the Science and Technology Facilities Council. These
-facilities operate pulsed neutron sources for scientific and industrial
-research, with many independent instruments receiving neutrons from a
-source for use in experiments.
-
-In both cases autoreduction was intended to serve as part of an
-automation system to handle data produced by these neutron beam
-instruments. However, the process is applicable to beamline instruments
-in general, such as might be used on muon or X-ray beams.
+The autoreduction implementation at ISIS uses the same underlying 
+technologies (choice of programming language and queue node software
+for example) as those used for the implementation of the SNS autoreduction
+service but differs in that its front end client is designed to serve
+autoreduction users only and in satisfying requirements of the ISIS 
+facility not orginally part of the SNS implementation.
 
@@
 it. Although the script itself need not change often, it may have
-configurable parameters -- variables -- which ought to be changed
-frequently.
+configurable parameters -- variables -- which might require more frequent
+updating.
 
@@
 appropriate script, with the correct variables, on them, supplying the
-reduced data to an archive for users to retrieve.
+reduced data to a data store for users to retrieve.
 
@@
 
-The system is intended primarily to serve the instrument scientists --
-who manage beamline instruments -- and users who use the instruments to
-run experiments. The key requirements for these users were to
+The system is intended to serve the instrument scientists (who manage beamline instruments) 
+and users who use the instruments to run experiments. 
+The key requirements from these users, which have been impleted to date, are:
 
@@
   Automate the reduction of data from beam instruments, using scripts
-  provided by instrument scientists.
+  provided by instrument scientists
 \item
   Show the status of reduction on runs, as well as the results and
-  locations of reduced data, to users.
+  locations of reduced data, to users
 \item
   Allow instrument scientists to set the parameters used for reduction,
-  in advance and retroactively.
+  in advance of experiments, and optionally schedule these to be diffirent
+  for particular experiment
 \item
   Allow users and instrument scientists to see what script, with which
-  parameters, was used to reduce a run.
+  parameters, was used to reduce a run
 \item
   Allow users and instrument scientists to modify the parameters used
-  for a run, and re-run reduction using new parameters or scripts.
+  for a run, and re-run reduction using new parameters or scripts
 \end{enumerate}
 
-Additional constraints were to
+Additionally, constraints are:
 
-\begin{enumerate}[noitemsep,resume]
+\begin{enumerate}[noitemsep]
 \item
   Limit access to the system to ensure that only staff and scientists
-  can access runs and instruments.
+  can access runs and instruments
 \item
   Utilise existing authentication systems to validate identities and
-  permissions for (1).
+  permissions for (1)
 \item
   Allow scalability for processing large amounts of data in a timely
-  manner.
-\item
-  Integrate with ICAT\cite{icat} -- the scientific metadata catalogue in use
-  at ISIS.
+  manner
 \end{enumerate}
@@
 \item
-  A listener for new jobs
+  A monitor for new instrument runs
 \item
@@
 
-When the listener detects that a new job should be created, it sends a
+When the monitor detects that a new run has completed on an instrument, it sends a
 request to do so to \emph{Data Ready}. The state database consumes the
-request and creates the corresponding job in the database, before
+request and creates a corresponding job in the database, before
 sending a request to process it to \emph{Reduction Pending}. The reduction
-worker takes this message and runs the appropriate script, sending the
+worker takes this message and executes the appropriate reduction script, sending the
 result to either \emph{Reduction Complete} or \emph{Reduction Error},
 where it's consumed by the state database to update the status of the
-run.
+job.
 
@@
 
-Data files typically run in the hundreds of MB at least, so would be
+Data files at ISIS typically run in the hundreds of MB, so would be
 impractical to send directly in a message; they're provided as file
@@
 
-\subsection{Job listener}\label{job-listener}
+\subsection{Run monitor}\label{run-monitor}
 
-When a new run has been completed on the beam line, the data files are
+When a new run has been completed on the beam line, the raw data files are
 placed in a shared filesystem. A node runs a Python watchdog daemon that
-tracks changes in this filesystem, and when a new run is added, sends a
-message to \emph{Data Ready} with details of the run. This particular
-choice of listener isn't crucial; anything would work as long as it
+tracks changes in this filesystem, and when a new run is detected, sends a
+message to \emph{Data Ready} with details of the run. The particular
+choice of monitor isn't crucial; anything would work as long as it
 pushed the same message to the queue. In the current production system
-at ISIS, this is the same node as the state database itself.
+at ISIS, the run monitor is on same node as the state database itself.
 
-\subsection{State database}\label{state-database}
+\subsection{State database \& coordinator}\label{state-database}
 
-A node keeps track of the status of runs in a local SQL database. This
+A node keeps track of the status of jobs in a local SQL database. This
 server hosts a Python service responsible for listening on \emph{Data
-Ready}, to create new runs and then dispatch them to \emph{Reduction
+Ready}, to create new jobs in the database and then dispatch them to \emph{Reduction
 Pending}. It manages variables for reduction, and selects the correct
-set for the run. The same server is responsible for serving the
-Python/Django\cite{django} web app. The database is therefore accessed through
-Django's object interface, and reduction runs, etc., are tracked as
-Django objects.
+set for the job. The same server is also responsible for serving the
+Python/Django\cite{django} web app, and the database is accessible through
+Django's object interface.
 
@@
 unavailable. Otherwise, it will proceed with the reduction, loading and
-then running the provided script.
+then running the provided reduction script.
 
-On a successful run, the job will notify \emph{Reduction Completed} with
+On a successful execuation, the daemon will notify \emph{Reduction Completed} with
 the location of the reduced data; otherwise, it will send the reason for
@@
 retry. In both cases it will send logs of the process, and clean up
-after itself. Some runs associated with the same experiment would write
+after itself. Some runs associated with the same experiment will write
 output to the same directory; to prevent clashes due to this, the node
-contains an internal queue holding all runs associated with an
-experiment for as long as it's actively reducing another run for the
+contains an internal queue holding all jobs associated with a given
+experiment for as long as it is actively reducing runs for the
 same experiment.
@@
 stored on a shared file store in a known location, where they can be
-modified at will by instrument scientists; runs store the script they
-were reduced by in the system database, but new runs will be reduced
-using the current script on the file store.
+modified at will by instrument scientists and the script used in
+reduction is stored in the system database.
 
@@
 such as calibration files, information about how the instrument was run,
-output settings, and so on. While some users prefer to hard-code these
-in their scripts, others would rather make use of a system for managing
-these variables separate from the script itself. A list of variables and
+output settings, and so on. A mechanism for providing such parameters 
+separate from the script itself is provided. A list of parameters and
 default values is provided in a Python file similar to the reduction
-script, but the autoreduction system keeps track of variable
-configurations provided to it through the web app, and applies them to
-the relevant runs.
+script, and the autoreduction system keeps track of the parameter
+configurations provided to it, and applies them to the relevant jobs.
 
-The reduction scripts need to integrate with the automation system, and
-as such must conform to a certain specification: the script must have a
-\emph{main()} method, taking an input file and an output directory as
-arguments. If the script uses system-supplied variables, it must have a
+The scripts need to integrate with the automation system, and
+as such must conform to a certain specification: a reduction script must have a
+\emph{main()} method, taking an input data file and an output directory as
+arguments. If the script uses system-supplied parameters, it must have a
 certain \emph{import} directive, which serves as a point of injection
-for the variables when it is run.
+for the variables when the reduction script is executed.
 
-Mantid provides a wrapper for data reduction through its Python
-interface, and for many instruments the whole reduction processing is
-also included. Writing reduction scripts for those instruments is
-essentially trivial, boiling down to some boilerplate with very little
-difference between instruments.
+A reduction script is a Python script and it can call any software 
+callable from Python installed on the reduction worker compute nodes,
+including Mantid data reduction algorithms.
+
+Each experiment at ISIS has a unique so-called RB-number
+and for almost all experiments at ISIS multiple separate runs are collected.
+A reduction script has access to all reduced data for an experiments, which 
+may be used in a script to automatically combine information from multiple 
+data reductions.
+
+at ISIS has access to previously reduced data can be a stupid and clever as an instrument
+scientists wants it to be. For example
 
@@
 It was developed in Python, using the Django web framework, and is
-tightly integrated with the state database.
+integrated (SHOULD WE BE MORE SPECIFIC ABOUT WHAT INTEGRATION
+MEANS HERE - THE READER MAY BE CONFUSED ABOUT THIS) with the state database.
 
@@
 governed by ICAT's information on the experiments and instruments they 
-should be able to see. A searchable index of runs is displayed on the front page, sorted
-by instrument, experiment and run number, showing their reduction
-status. Runs, experiments and instruments displayed here have links to
-their summary pages.
+should be able to see. A searchable index of the runs is displayed on the front page, sorted
+by instrument, experiment (RB-number) and/or run number, showing their reduction
+status.
 
@@
 be re-run, with or without modifying the variables used. Any
-experimenter can access this page for their runs, and it's intended that
+experimenter can access this page for their runs, and it is intended that
 external scientists running experiments be able to control their data
@@
 sets of variables by experiment and run number, which will then be used
-automatically as appropriate for new runs. Batch re-running of past jobs
-is also possible here. This is intended to be the main point of access
-for instrument scientists to control data reduction.
+for new runs. Batch re-running of past jobs
+is also possible here. This option allows instrument scientists
+the convenience of re-running multiple failed jobs should this be required.
 
@@
 
-\section{Current status}\label{current-status}
+\section{Deployment}\label{deployment}
 
-The system is deployed at ISIS, in limited use. The frontend node, managing
-the state and web app, is a Windows Server system running on a 
+The system is deployed at ISIS. The node managing
+the state and web app is a Windows Server system running on a 
 Hyper-V\cite{hyper-v} virtualisation cluster; it serves the web app using
 Microsoft's Internet Information Services (IIS)\cite{iis} and 
-FastCGI\cite{fcgi}.
+FastCGI\cite{fcgi}. The web app is currently only accessible from inside
+the laboratory using the URL: http://reduce.isis.cclrc.ac.uk.
 
 There is one reduction node, running Red Hat Enterprise Linux 7\cite{rhel}
-on a dedicated server -- reducing large amounts of data is very CPU-intensive.
+on a dedicated server -- reducing large amounts of data is memory and CPU-intensive.
 This node also serves the message queue; subsequent worker nodes would
-not have multiple message queues, and it would be wise to separate the
-message queue from the worker entirely in this case.
+not have multiple message queues, and the message queue will be hosted
+on a separate node.
+
+The software written as part this project is not tied to a
+particular operating system since it is written entirely in Python and Django.
+
+\section{Future plans}\label{future-plans}
 
 It is planned that the autoreduction system be developed to further meet
-the needs and tastes of potential users at ISIS and other particle
-facilities, and enter a more prominent role in automating data
-processing there. Future development to this end may involve
+the needs of users. Future development to this will involve:
 
@@
   Expanding the system to accommodate greater volume of use -- this
-  might involve accomodating more reduction workers, for example.
+  might involve accomodating more reduction workers, for example
 \item
-  Integrating other methods of listening for new runs -- the current
-  method of watching a file archive is specific to ISIS.
+  Integrating other methods of monitoring or listening for new runs -- the current
+  method of watching a file archive is specific to ISIS
+\item
+  Make the web app to be accessible from outside of the laboratory
+\item
+  Have selected reduced data automatically cataloqued in ICAT 
 \item
   Improving portability and deployability of the current software; the
-  state database/webapp in particular is currently unsupported for
-  Linux, and the whole system is somewhat nontrivial to deploy even to a
-  development environment.
+  state database/webapp is currently somewhat nontrivial to deploy
 \end{enumerate}
+
+Longer term, the system may be extended to listen to live streams and starts
+processing such data as they come off beamlines rather then waiting for files 
+to be written to disk.
 
@@
 frontend to allow users to control the reduction process manually and verify
-that the correct reduction was run.
+that the correct reduction was executed.
 
-The system is currently in limited use at ISIS, with more instrument scientists
-interested in using it. The source code can be found on GitHub\cite{source}.
+The source code can be found on GitHub\cite{source}.
+
+\section{Acknowledgement}\label{Acknowledgement}
+
+Tom Griffin, Nick Draper, Martyn Gigg, Alex Buts, other excitation group members and other testers, Shelly Ren and Mathieu Doucet.
 
@@
     \href{http://dx.doi.org/10.1016/j.nima.2014.07.029}{10.1016/j.nima.2014.07.029}.
+
+\bibitem{autoreduceSNS}
+    G. Shipman, et al.,
+    \emph{Accelerating Data Acquisition, Reduction, and Analysis at the Spallation Neutron Source},
+    2014 IEEE 10th International Conference on eScience, Volume 2, 11 November 2014, Pages 224-230,
+    \href{http://dx.doi.org/10.1109/eScience.2014.31}{10.1109/eScience.2014.31}.
 

### 2017-07-10 autoreduce_webapp/reduction_viewer/utils.py
Reset the modification time when retrying a run #344

@@ -90,7 +90,10 @@ class ReductionRunUtils(object):
         If a script (as a string) is supplied then use it, otherwise use the previous run's.
         """
         from reduction_variables.utils import InstrumentVariablesUtils, VariableUtils
-		
+
+        # Get the current last_updated value as we'll need it when resetting it later on.
+        run_last_updated = reductionRun.last_updated
+
         if username == 'super':
             username = 1
 
@@ -119,6 +122,10 @@ class ReductionRunUtils(object):
             reductionRun.retry_run = new_job
             reductionRun.retry_when = timezone.now().replace(microsecond=0) + datetime.timedelta(seconds=delay if delay else 0)
             reductionRun.save()
+
+            # Saving the reduction run in the previous step will also have incremented the last_updated value for the
+            # previous run. Since we want to keep this the same, we can manually update the value ourselves.
+            ReductionRun.object.filter(id = reductionRun.id).update(last_updated = run_last_updated)
             
             # copy the previous data locations
             for data_location in reductionRun.data_location.all():
@@ -138,9 +145,7 @@ class ReductionRunUtils(object):
             return new_job
             
         except Exception as e:
-            logger.error('Hello!')
             logger.error(e.message)
-            logger.error('Goodbye!')
             new_job.delete()
             raise
             

### 2017-07-11 autoreduce_webapp/autoreduce_webapp/backends.py
Added a development option in the settings for #343

@@ -1,17 +1,16 @@
 from autoreduce_webapp.uows_client import UOWSClient
 from autoreduce_webapp.icat_cache import ICATCache
-from django.conf import settings
 from django.contrib.auth.models import User
-from urllib2 import URLError
-from settings import LOG_FILE, LOG_LEVEL, UOWS_URL
 import logging
 logger = logging.getLogger(__name__)
+
 
 class UOWSAuthenticationBackend(object):
     """
     Custom authentication for use with the User Office Web Service
     """
-    def authenticate(self, token=None):
+    @staticmethod
+    def authenticate(token=None):
         """
         Checks that the given session ID (token) is still valid and returns an appropriate user object.
         If this is the first time a user has logged in a new user object is created.
@@ -23,7 +22,11 @@ class UOWSAuthenticationBackend(object):
                 try:
                     user = User.objects.get(username=person['usernumber'])
                 except User.DoesNotExist:
-                    user = User(username=person['usernumber'], password='get from uows', first_name=person['first_name'], last_name=person['last_name'], email=person['email'])
+                    user = User(username=person['usernumber'],
+                                password='get from uows',
+                                first_name=person['first_name'],
+                                last_name=person['last_name'],
+                                email=person['email'])
 
                 with ICATCache() as icat:
                     # Make sure user has correct permissions set. This will be checked upon each login
@@ -34,7 +37,8 @@ class UOWSAuthenticationBackend(object):
 
         return None
 
-    def get_user(self, user_id):
+    @staticmethod
+    def get_user(user_id):
         try:
             return User.objects.get(pk=user_id)
         except User.DoesNotExist:

### 2017-07-11 autoreduce_webapp/autoreduce_webapp/daemon.py

@@ -3,9 +3,13 @@
     Code taken from:
     http://www.jejik.com/articles/2007/02/a_simple_unix_linux_daemon_in_python/
 """
-import sys, os, time, atexit
+import sys
+import os
+import time
+import atexit
 from signal import SIGTERM 
 import logging
+
 
 class Daemon(object):
     """
@@ -63,9 +67,9 @@ class Daemon(object):
         # write pidfile
         atexit.register(self.delpid)
         pid = str(os.getpid())
-        file(self.pidfile,'w+').write("%s\n" % pid)
+        file(self.pidfile, 'w+').write("%s\n" % pid)
         logging.info("Started daemon with PID %s" % str(pid))
-    
+
     def delpid(self):
         os.remove(self.pidfile)
 
@@ -75,7 +79,7 @@ class Daemon(object):
         """
         # Check for a pidfile to see if the daemon already runs
         try:
-            pf = file(self.pidfile,'r')
+            pf = file(self.pidfile, 'r')
             pid = int(pf.read().strip())
             pf.close()
         except IOError:
@@ -88,7 +92,7 @@ class Daemon(object):
         
         # Start the daemon
         self.daemonize()
-        self.run()
+        self.run(self)
 
     def stop(self):
         """
@@ -96,7 +100,7 @@ class Daemon(object):
         """
         # Get the pid from the pidfile
         try:
-            pf = file(self.pidfile,'r')
+            pf = file(self.pidfile, 'r')
             pid = int(pf.read().strip())
             pf.close()
         except IOError:
@@ -105,7 +109,7 @@ class Daemon(object):
         if not pid:
             message = "pidfile %s does not exist. Daemon not running?\n"
             logging.error(message % self.pidfile)
-            return # not an error in a restart
+            return  # not an error in a restart
 
         logging.info("Stopping daemon with PID %s" % str(pid))
 
@@ -130,6 +134,7 @@ class Daemon(object):
         self.stop()
         self.start()
 
+    @staticmethod
     def run(self):
         """
         You should override this method when you subclass Daemon. It will be called after the process has been

### 2017-07-11 autoreduce_webapp/autoreduce_webapp/icat_cache.py

@@ -1,19 +1,23 @@
-import datetime, logging
-logger = logging.getLogger("app")
+import datetime
+import logging
 from django.utils import timezone
 from autoreduce_webapp.settings import CACHE_LIFETIME
 from autoreduce_webapp.icat_communication import ICATCommunication
 from autoreduce_webapp.models import UserCache, InstrumentCache, ExperimentCache
 
+logger = logging.getLogger("app")
+
 
 class ICATConnectionException(Exception):
     pass
 
+
 class ICATCache(object):
     """
     A wrapper for ICATCommunication that caches information, and in the case of ICAT failure will try to use this cache.
-    It stores Cache models in the database, and will get all fields from ICATCommunication if a model is requested but has expired or doesn't exist.
-    Most of the methods it wraps from ICATCommunication are templated rather than declared explicitly; see below.    
+    It stores Cache models in the database, and will get all fields from ICATCommunication if a model is requested but
+    has expired or doesn't exist. Most of the methods it wraps from ICATCommunication are templated rather than declared
+    explicitly; see below.
     """
     def __init__(self, **kwargs):
         self.kwargs = kwargs
@@ -23,7 +27,7 @@ class ICATCache(object):
     def __enter__(self):
         return self
 
-    def __exit__(self, type, value, traceback):
+    def __exit__(self, value, traceback):
         if self.icat is not None:
             self.icat.__exit__(type, value, traceback)
             
@@ -33,20 +37,21 @@ class ICATCache(object):
             if self.icat is None:
                 self.icat = ICATCommunication(**self.kwargs)
         except Exception as e:
-            logger.error("Failed to connect to ICAT: %s - %s" % (type(e).__name, e))
+            logger.error("Failed to connect to ICAT: %s - %s" % (type(e), e))
             raise ICATConnectionException()
             
     def is_valid(self, cache_obj):
         """ Check whether a cache object is fresh and is not None. """
         return cache_obj and cache_obj.created + datetime.timedelta(seconds=self.cache_lifetime) > timezone.now()
-        
-    def to_list(self, l):
+
+    @staticmethod
+    def to_list(l):
         return ",".join(map(str, l))
             
-    def cull_invalid(self, list):
+    def cull_invalid(self, validity_list):
         """ Removes all objects in the list that have expired. """
         rlist = []
-        for obj in list:
+        for obj in validity_list:
             obj.delete() if not self.is_valid(obj) else rlist.append(obj)
         return rlist
         
[…]

### 2017-07-11 autoreduce_webapp/autoreduce_webapp/settings.py

@@ -1,4 +1,3 @@
-import logging
 import os
 BASE_DIR = os.path.dirname(os.path.dirname(__file__))
 
@@ -207,3 +206,4 @@ FACILITY = "ISIS"
 PRELOAD_RUNS_UNDER = 100 # If the index run list has fewer than this many runs to show the user, preload them all.
 CACHE_LIFETIME = 3600 # Objects in ICATCache live this many seconds when ICAT is available to update them.
 USER_ACCESS_CHECKS = True # Should the webapp prevent users from accessing runs/instruments they're not allowed to?
+DEVELOPMENT_MODE = True

### 2017-07-11 autoreduce_webapp/autoreduce_webapp/view_utils.py

@@ -7,12 +7,14 @@ from reduction_viewer.models import ReductionRun, Experiment
 from django.template import RequestContext
 from django.shortcuts import render_to_response
 from reduction_viewer.models import Notification, Setting
+from settings import DEVELOPMENT_MODE
 
 def has_valid_login(request):
     """
     Check that the user is correctly logged in and their session is still considered valid
     """
-    return True
+    if DEVELOPMENT_MODE:
+        return True
     if request.user.is_authenticated() and 'sessionid' in request.session and UOWSClient().check_session(request.session['sessionid']):
         return True
     return False
@@ -78,7 +80,7 @@ def render_with(template):
                 output['notifications'] = notifications
             else:
                 output['notifications'].extend(notifications)
-            '''
+
             if 'bad_browsers' not in output:
                 # Load in the list of not accepted browsers from the settings
                 bad_browsers = []
@@ -109,7 +111,7 @@ def render_with(template):
                 output['current_browser'] = family
                 output['version'] = version
                 output['outdated'] = outdated
-	    '''
+
             if 'reduction_variables_on' not in output:
                 output['reduction_variables_on'] = ('reduction_variables' in INSTALLED_APPS)
             

### 2017-07-11 autoreduce_webapp/reduction_variables/utils.py

@@ -16,8 +16,13 @@ def log_error_and_notify(message):
     Helper method to log an error and save a notifcation
     """
     logger.error(message)
-    notification = Notification(is_active=True, is_staff_only=True, severity='e', message=message)
-    notification.save()
+
+    # Only want to save the notification if there is no message like it already. Otherwise one message could spam the
+    # front page.
+    existing_notifications = Notification.objects.filter(message=message)
+    if existing_notifications == []:
+        notification = Notification(is_active=True, is_staff_only=True, severity='e', message=message)
+        notification.save()
 
 class VariableUtils(object):
     def derive_run_variable(self, instrument_var, reduction_run):

### 2017-07-11 autoreduce_webapp/reduction_viewer/views.py

@@ -6,7 +6,7 @@ from django.core.exceptions import PermissionDenied
 from django.db.models import Q
 from autoreduce_webapp.uows_client import UOWSClient
 from autoreduce_webapp.icat_cache import ICATCache
-from autoreduce_webapp.settings import UOWS_LOGIN_URL, PRELOAD_RUNS_UNDER, USER_ACCESS_CHECKS
+from autoreduce_webapp.settings import UOWS_LOGIN_URL, PRELOAD_RUNS_UNDER, USER_ACCESS_CHECKS, DEVELOPMENT_MODE
 from reduction_viewer.models import Experiment, ReductionRun, Instrument
 from reduction_viewer.utils import StatusUtils, ReductionRunUtils
 from reduction_viewer.view_utils import deactivate_invalid_instruments
@@ -26,13 +26,16 @@ def index(request):
     use_query_next = request.build_absolute_uri(request.GET.get('next'))
     default_next = 'run_list'
 
-    user = authenticate(username="super", password="super")
-    login(request, user)
+    authenticated = False
 
-    logger.info('Super user logging in')
-    logger.info(user.username)
-    if True:
-    # if request.user.is_authenticated() and 'sessionid' in request.session and UOWSClient().check_session(request.session['sessionid']):
+    if DEVELOPMENT_MODE:
+        user = authenticate(username="super", password="super")
+        login(request, user)
+        authenticated = True
+    else:
+        authenticated = request.user.is_authenticated() and 'sessionid' in request.session and UOWSClient().check_session(request.session['sessionid'])
+
+    if authenticated:
         if request.GET.get('next'):
             return_url = use_query_next
         else:
@@ -150,8 +153,7 @@ def run_list(request):
     instruments = []
     owned_instruments = []
     experiments = {}
-    logger.info('Super user')
-    logger.info(request.user.username)
+
     # Superuser sees everything
     if request.user.is_superuser or not USER_ACCESS_CHECKS:
         instrument_names = Instrument.objects.values_list('name', flat=True)

### 2017-07-11 Documentation/paper/paper.tex
Added name and paragraph about reduction to paper

@@
 \title{\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}}
-\author{J. R. Corderoy, L. Greenwood, M. Noble, D. Oram and A. J. Markvardsen (code contributors)\\
+\author{J. R. Corderoy, T. Gowland, L. Greenwood, M. Noble, D. Oram and A. J. Markvardsen \\
+(code contributors)\\
 ISIS Facility, Rutherford Appleton Laboratory\\
@@
 processing of instrument data before use. Autoreduction is a software
-system designed to automate this process, integrated with other
+system designed to automate this process, integrate with other
 pre-existing facility systems and software packages, and provide
@@
 This article describes the system setup for Autoreduction at the ISIS Facility;
-it motivation and design, its use and interface, and its current status in production at ISIS.
+its motivation and design, its use and interface and its current status in production at ISIS.
 
@@
 `reduce' -- raw data collected from an instrument into a form
-that a user can interprete or can do further analysis on. For example
+that users can interprete or do further analysis on. For example
 by removing instrument specific artifacts from the measured data, 
 transforming the data into different units and/or
-into data formats readably by further analysis software.
+into data formats readable by further analysis software.
 
 The purpose of the autoreduction system is to provide a useful automation
-step in this process. The system described in this works allows data coming 
+step in this process. The system described in this paper allows data coming 
 off an instrument to be automatically reduced using a dedicated software package 
-such as Mantid\cite{mantid}, while lending transparency to the process and
+such as Mantid\cite{mantid}, whilst also lending transparency to the process and
 letting users control it through a straightforward web interface.
 
-TO DO: some reference that automation of data reduction also persued at
-other large scale facilities: Anders writing from NOBUGS conference: such as 
-possibly mention Diamand has a batch script based system 
-for macromolecular beamlines (talk by Dr Markus Gerstel, Diamond). Dr Martin Rehr 
-mentioned in his talk on "Image data Management System" that auto processing was
-used. Dr Sergey Stepanov talk "Integration of fast detectors into.... macromolecular
-crystallography beamlines at the Advanced Photon Source" used auto processing - seemed
-to be a theme for MX beamlines.
+Automated data reduction is a concept which is actively persued at other large facilities.
+At the NOBUGS 2016 Conference\cite{NOBUGS}, there were several talks given by delegates
+from other large scale facilities which mentioned the automated reduction of data at a variety
+of facilities.
+
+Data Analysis Infrastructure for DLS MX/CX \cite{dls-talk} discusses a batch
+script based system for macromolecular beamlines. It makes use of ActiveMQ \cite{activemq}
+(which will be discussed later in this paper) and also has a front end status monitor to
+show the health of the system during run-time. Integration of Fast Detectors 
+into Beamline Control \cite{anl-talk} also mentioned the use of automatic data processing.
+To keep up with the data rates from faster detectors, they are now automatically reducing data
+immediately so that users can see the results as soon as the dataset is taken.
 
@@
 The autoreduction system at ISIS was inspired by an autoreduction setup at the
-the Spallation Neutron Source (SNS) at Oak Ridge National Laboratory \cite{autoreductionSNS}.
+the Spallation Neutron Source (SNS) at Oak Ridge National Laboratory \cite{autoreduceSNS}.
 
@@
 for example) as those used for the implementation of the SNS autoreduction
-service but differs in that its front end client is designed to serve
-autoreduction users only and in satisfying requirements of the ISIS 
-facility not orginally part of the SNS implementation.
+service. However, the ISIS implementation differs in that its front end 
+client is designed to serve autoreduction users only and was not orginally 
+part of the SNS implementation.
 
@@
 service of experiments. This raw data typically needs to be processed --
-`reduced' -- before it can be used by scientists, by running a script on
-it. Although the script itself need not change often, it may have
+`reduced' -- before it can be used by scientists. This is done by running a 
+script on it. Although the script itself need not change often, it may have
 configurable parameters -- variables -- which might require more frequent
@@
 The autoreduction system is intended to automate this process.
-Instrument scientists provide it with reduction scripts - in a specified
-location on a shared file archive - and sets of variables to use to
-reduce runs. The system watches for the completion of runs, and runs the
-appropriate script, with the correct variables, on them, supplying the
-reduced data to a data store for users to retrieve.
+Instrument scientists provide the system with reduction scripts - in a specified
+location on a shared file archive - along with sets of variables to use to
+reduce runs. Firstly, the system watches  for the completion of runs. Once a new
+completed run has been found, the system will then run the appropriate script
+with the correct variables on the new run. Once the script has finished execution,
+reduced data will be saved to a data store for users to retrieve.
 
@@
 and users who use the instruments to run experiments. 
-The key requirements from these users, which have been impleted to date, are:
+The key requirements from these users, which have been completed to date, are:
 
@@
 \item
-  Allow instrument scientists to set the parameters used for reduction,
-  in advance of experiments, and optionally schedule these to be diffirent
+  Allow instrument scientists to set the parameters used for reduction
+  in advance of experiments and optionally schedule these to be diffirent
   for particular experiment
 \item
-  Allow users and instrument scientists to see what script, with which
-  parameters, was used to reduce a run
+  Allow users and instrument scientists to see what script and with which
+  parameters was used to reduce a run
 \item
   Allow users and instrument scientists to modify the parameters used
-  for a run, and re-run reduction using new parameters or scripts
+  for a run and re-run reduction using new parameters or scripts
 \end{enumerate}
 
-Additionally, constraints are:
+Additional constraints are:
 
@@
 
-The architecture is based on a queue node, which co-ordinates
+The architecture is based on a queue node which co-ordinates
 communication between all components of the system. This maintains
-separate message queues, which allow components to act on messages from
-other components and update the system. These components are
+separate message queues which allow components to act on messages from
+other components and update the system. These components are:
 
@@
 
+\bibitem{dls-talk}
+	M. Gerstel, R. Gildea, K. Levik, A. Ashton, G. Winter.
+	\emph{Data Analysis Infrastructure for DLS MX/CX},
+	NOBUGS Conference 2016, Københavns Universitet,
+	\url{https://indico.esss.lu.se/event/357/session/7/contribution/51/material/slides/0.pdf}
+
+\bibitem{anl-talk}
+	Dr. Sergey Stepanov.
+	\emph{Integration of fast detectors into beamline controls at the GM/CA macromolecular crystallography beamlines at the Advanced Photon Source},
+	NOBUGS Conference 2016, Københavns Universitet,
+	\url{https://indico.esss.lu.se/event/357/session/6/contribution/17/material/slides/0.pdf}
+
+\bibitem{NOBUGS}
+	NOBUGS Conference 2016,
+	\emph{NOBUGS},
+	\url{https://indico.esss.lu.se/event/357/}.
+
 \bibitem{django}

### 2017-07-11 Documentation/paper/paper.tex
Removed border around reference numbers

@@
 
-\usepackage[unicode=true]{hyperref}
+\usepackage[unicode=true, hidelinks]{hyperref}
 \usepackage{enumitem}
 \usepackage{graphicx,grffile}
+\usepackage{xcolor}
+\hypersetup{
+	colorlinks,
+	linkcolor={red!50!black},
+	citecolor={blue!50!black},
+	urlcolor={blue!80!black}
+}
 
@@
 off an instrument to be automatically reduced using a dedicated software package 
-such as Mantid\cite{mantid}, whilst also lending transparency to the process and
+such as Mantid \cite{mantid}, whilst also lending transparency to the process and
 letting users control it through a straightforward web interface.
@@
 Automated data reduction is a concept which is actively persued at other large facilities.
-At the NOBUGS 2016 Conference\cite{NOBUGS}, there were several talks given by delegates
+At the NOBUGS 2016 Conference \cite{NOBUGS}, there were several talks given by delegates
 from other large scale facilities which mentioned the automated reduction of data at a variety

### 2017-07-11 Documentation/paper/paper.tex
Updated description of message queue system

@@
 
-When the monitor detects that a new run has completed on an instrument, it sends a
-request to do so to \emph{Data Ready}. The state database consumes the
-request and creates a corresponding job in the database, before
-sending a request to process it to \emph{Reduction Pending}. The reduction
-worker takes this message and executes the appropriate reduction script, sending the
-result to either \emph{Reduction Complete} or \emph{Reduction Error},
-where it's consumed by the state database to update the status of the
-job.
+When the monitor detects that a new run has completed on an instrument, it will send a 
+message to the \emph{Data Ready} queue. The \emph{QueueProcessor} process will consume this
+message, strip out the relevant information and creates a corresponding job in the database.
+\emph{QueueProcessor} will then send the message on to the \emph{Reduction Pending} queue.
+The \emph{AutoreductionProcessor} process will be watching the \emph{Reduction Pending} queue.
+When \emph{AutoreductionProcessor} recieves a message, it runs the \emph{PostProcessAdmin} 
+script which will send a message to the \emph{ReductionStarted} queue such that the database
+remains up to date. Once reduction has finished, \emph{PostProcessAdmin}  will send the
+result to either \emph{Reduction Complete} or \emph{Reduction Error} where it will be consumed
+by the \emph{QueueProcessor} and updated in the database.
 
@@
 
-Apache ActiveMQ\cite{activemq} is used as the message queueing system, with
-message contents as JSON-formatted objects. The intention of the message
-is conveyed by which queue it's placed in, rather than a field in the
+Apache ActiveMQ \cite{activemq} is used as the message queueing system using 
+JSON-formatted objects as messages. The intention of the message
+is conveyed by which queue it's placed in rather than a field in the
 message itself. Runs can be `scheduled' simply by using ActiveMQ's
-scheduled delay feature, which allows a message to be delivered a given
+scheduled delay feature which allows a message to be delivered a given
 time after it's been pushed to the queue.
@@
 
-Data files at ISIS typically run in the hundreds of MB, so would be
-impractical to send directly in a message; they're provided as file
+Data files at ISIS typically run in the hundreds of MB. They are therefore 
+impractical to be sent directly in a message and instead they're provided as file
 paths on a shared file archive. Meanwhile, the reduction script to be
-used is sent as a string; the script is served from the state database,
-and using the message queue directly to send it obviates the need to
+used is sent as a string; the script is served from the state database
+and using the message queue to directly send it obviates the need to
 rely on a potentially flaky shared file store within the system.
@@
 placed in a shared filesystem. A node runs a Python watchdog daemon that
-tracks changes in this filesystem, and when a new run is detected, sends a
+tracks changes in this filesystem and, when a new run is detected, will send a
 message to \emph{Data Ready} with details of the run. The particular

### 2017-07-12 Documentation/paper/paper.tex
Updated state database section

@@
 
-A node keeps track of the status of jobs in a local SQL database. This
-server hosts a Python service responsible for listening on \emph{Data
-Ready}, to create new jobs in the database and then dispatch them to \emph{Reduction
-Pending}. It manages variables for reduction, and selects the correct
-set for the job. The same server is also responsible for serving the
-Python/Django\cite{django} web app, and the database is accessible through
-Django's object interface.
+The \emph{QueueProcessor} service runs as a daemon and is the service responsible
+for keeping track of the status of jobs in an SQL database. The service
+listens on the \emph{Data Ready} queue. When messages are first received,
+the service will set the correct variables for the job, create new jobs in 
+the database and, when ready, will send a message to the \emph{Reduction Pending} queue.
 
-The daemon receives status updates from reduction workers on
-\emph{Reduction Started}, \emph{Reduction Complete} and \emph{Reduction
-Error}, making the appropriate changes to the database. On some messages
-in the error queue, the daemon will create and schedule the appropriate
-retry runs. A system for emailing notifications of run failures to
-administrators is also implemented here.
+The daemon service also receives updates from the reduction worker itself. When the 
+reduction worker reaches certain stages of its execution, it will send messages to
+\emph{Reduction Started}, \emph{Reduction Complete} and \emph{Reduction Error}.
+The \emph{QueueProcessor} service also listens on these queues and will update the database
+accordingly when messages are received. For some messages in the error queue, the daemon 
+will create and schedule the appropriate retry runs. There is also a system in place for 
+emailing notifications of run failures to administrators.
+
+Since the database is being frequently being updated throughout the process of autoreduction,
+the Python/Django\cite{django} WebApp is always up to date with the latest information.
+This means that users can easily check on the progress of their runs and get a good idea of 
+how long it is going to take for them to retrieve their data at the end.
 

### 2017-07-12 Documentation/paper/paper.tex
Minor grammar changes and adding ICAT citation

@@
 
-On a successful execuation, the daemon will notify \emph{Reduction Completed} with
+On a successful execution, the daemon will notify \emph{Reduction Completed} with
 the location of the reduced data; otherwise, it will send the reason for
 failure to \emph{Reduction Error}, most likely without triggering a
-retry. In both cases it will send logs of the process, and clean up
+retry. In both cases, it will create logs of the process and also clean up
 after itself. Some runs associated with the same experiment will write
@@
 using the Mantid software package to do the heavy lifting. They're
-stored on a shared file store in a known location, where they can be
-modified at will by instrument scientists and the script used in
-reduction is stored in the system database.
+stored on a shared file store in a known location where they can be
+modified at will by instrument scientists. The script used in
+reduction is also stored in the system database.
 
@@
 default values is provided in a Python file similar to the reduction
-script, and the autoreduction system keeps track of the parameter
-configurations provided to it, and applies them to the relevant jobs.
+script. The autoreduction system keeps track of the parameter
+configurations provided to it and applies them to the relevant jobs.
 
@@
 arguments. If the script uses system-supplied parameters, it must have a
-certain \emph{import} directive, which serves as a point of injection
+certain \emph{import} directive which serves as a point of injection
 for the variables when the reduction script is executed.
@@
 A reduction script is a Python script and it can call any software 
-callable from Python installed on the reduction worker compute nodes,
-including Mantid data reduction algorithms.
+callable from Python installed on the reduction worker compute nodes which
+includes Mantid data reduction algorithms.
 
@@
 and for almost all experiments at ISIS multiple separate runs are collected.
-A reduction script has access to all reduced data for an experiments, which 
+A reduction script has access to all reduced data for an experiment, which 
 may be used in a script to automatically combine information from multiple 
 data reductions.
-
-at ISIS has access to previously reduced data can be a stupid and clever as an instrument
-scientists wants it to be. For example
 
@@
 It was developed in Python, using the Django web framework, and is
-integrated (SHOULD WE BE MORE SPECIFIC ABOUT WHAT INTEGRATION
-MEANS HERE - THE READER MAY BE CONFUSED ABOUT THIS) with the state database.
+integrated with the state database. Django provides an intuitive way to
+interact with databases through its use of models and Object Relational Mapping (ORM).
+Therefore, getting information from the database to show on the front end is 
+quick and intuitive.
 
@@
 granted for facility-wide use -- and their level of access is then 
-governed by ICAT's information on the experiments and instruments they 
+governed by ICAT's \cite{icat} information on the experiments and instruments they 
 should be able to see. A searchable index of the runs is displayed on the front page, sorted
@@
 script and variables that were used to reduce it. From here the run can
-be re-run, with or without modifying the variables used. Any
+be re-run, with or without modifying the variables used and with the choice
+of whether or not to overwrite the previous run's data. Any
 experimenter can access this page for their runs, and it is intended that
-external scientists running experiments be able to control their data
+external scientists running experiments would be able to control their data
 reduction directly in this way.
 
-Experiments also have summary pages, showing all the runs that are
+Experiments also have summary pages, showing all of the runs that are
 associated with a given experiment along with their status and data
@@
 showing the current status of runs on an instrument, as well as current
-and upcoming run variables. From here instrument scientists can assign
-sets of variables by experiment and run number, which will then be used
-for new runs. Batch re-running of past jobs
-is also possible here. This option allows instrument scientists
-the convenience of re-running multiple failed jobs should this be required.
+and upcoming run variables. From here, instrument scientists can assign
+sets of variables by experiment and run number which will then be used
+for new runs. Batch re-running of past jobs is also possible here. 
+This option allows instrument scientists the convenience of re-running multiple 
+failed jobs should this be required.
 
-Administrators can access everything above, and additionally have access
+Administrators can access everything above and additionally have access
 to pages displaying all queued and failed jobs. These pages provide an
-overview of the status of the system at a glance, and have controls for
+overview of the status of the system at a glance and have controls for
 batch operations on failed jobs such as to re-run them.

### 2017-07-12 Documentation/paper/paper.tex
Updated deployment section

@@
 
-The system is deployed at ISIS. The node managing
-the state and web app is a Windows Server system running on a 
-Hyper-V\cite{hyper-v} virtualisation cluster; it serves the web app using
-Microsoft's Internet Information Services (IIS)\cite{iis} and 
-FastCGI\cite{fcgi}. The web app is currently only accessible from inside
-the laboratory using the URL: http://reduce.isis.cclrc.ac.uk.
+The system is deployed at ISIS. The node managing the WebApp is a Windows Server 2012
+running on a Hyper-V\cite{hyper-v} virtualisation cluster and it serves the WebApp using
+Apache's HTTP Server\cite{apache}. The WebApp runs on a Windows server for security reasons
+but since it runs on a basic Apache server, it could easily be moved across to a Linux machine
+if it needed to. The WebApp is currently only accessible from inside the laboratory using the 
+URL: http://reduce.isis.cclrc.ac.uk.
 
-There is one reduction node, running Red Hat Enterprise Linux 7\cite{rhel}
-on a dedicated server -- reducing large amounts of data is memory and CPU-intensive.
-This node also serves the message queue; subsequent worker nodes would
-not have multiple message queues, and the message queue will be hosted
-on a separate node.
+There is then a second node which runs Red Hat Enterprise Linux 7\cite{rhel}. This node
+manages the parts of the system which are common between front and backend. This includes:
+the MySQL database, the ActiveMQ server and the EndOfRunMonitor. This node should have
+all the parts of the system that wouldn't need to be replicated as part of a worker node.
+
+The third and final node manages the parts of the system that could be replicated such that 
+we can have multiple worker nodes active in order to split the load of autoreduction and speed
+up the overall process. This node has the QueueProcessor and the AutoreductionProcessor installed
+on it. At the moment, the production system only uses one of these nodes but as the usage of the 
+system increases, so too will the load. It might then be sensible to have multiple worker nodes.
+
+The system is split out in this way such that if the machine with the WebApp installed were to fail,
+the overall process of reduction could still take place. We would still pick up new runs with the 
+EndOfRunMonitor and would still be able to process them with QueueProcessor and AutoreductionProcessor.
 
@@
 \item
-  Make the web app to be accessible from outside of the laboratory
+  Make the WebApp accessible from outside of the laboratory
 \item
-  Have selected reduced data automatically cataloqued in ICAT 
+  Have selected reduced data automatically catalogued in ICAT 
 \item
@@
   state database/webapp is currently somewhat nontrivial to deploy
+\item 
+  Having the worker node machine as a Docker \cite{docker} image for
+  easier deployment
 \end{enumerate}
 
-Longer term, the system may be extended to listen to live streams and starts
-processing such data as they come off beamlines rather then waiting for files 
+In the longer term, the system may be extended to listen to live streams and begin
+processing data as soon as it comes off beamlines rather then waiting for files 
 to be written to disk.
@@
 on beamline instruments. It uses a scalable architecture to allow prompt
-reduction of data from a large number of instruments, and utilises a web app
+reduction of data from a large number of instruments and utilises a web app
 frontend to allow users to control the reduction process manually and verify
@@
 
+\bibitem{apache}
+	Apache HTTP Server Project
+	\emph{Apache},
+	\url{https://httpd.apache.org/}.
+
 \bibitem{hyper-v}
@@
     \url{https://technet.microsoft.com/en-us/library/mt169373.aspx}.
+
+\bibitem{Docker}
+	Docker,
+	\emph{Docker},
+	\url{https://www.docker.com/}
 

### 2017-07-14 autoreduce_webapp/autoreduce_webapp/icat_cache.py
Changed use of icat_cache to use icat_communication instead

@@ -66,6 +66,7 @@ class ICATCache(object):
             # Check func_list for the attributes that each model should have, and the corresponding ICATCommunication
             # function to query for it; call it for each, building a dict, and then splice it into the constructor
             # kwargs.
+
             new_obj = obj_type(**{attr: (getattr(self.icat, func)(obj_id) if typ is None else self.to_list(getattr(self.icat, func)(obj_id))) for (func, model, attr, typ) in func_list if model == obj_type})
         else:
             # In this case, ICATCommunication returns all the ExperimentCache fields in one query,

### 2017-07-14 autoreduce_webapp/autoreduce_webapp/icat_communication.py

@@ -1,4 +1,4 @@
-from settings import LOG_FILE, LOG_LEVEL, ICAT, BASE_DIR
+from settings import ICAT, BASE_DIR
 import logging, os, sys, datetime
 logger = logging.getLogger(__name__)
 from sets import Set

### 2017-07-14 autoreduce_webapp/autoreduce_webapp/settings.py

@@ -44,7 +44,7 @@ MIDDLEWARE_CLASSES = (
 )
 
 AUTHENTICATION_BACKENDS = (
-    #'autoreduce_webapp.backends.UOWSAuthenticationBackend',
+    'autoreduce_webapp.backends.UOWSAuthenticationBackend',
     'django.contrib.auth.backends.ModelBackend',
 )
 LOGIN_URL = '/'
@@ -68,7 +68,7 @@ DATABASES = {
         'NAME': 'autoreduction',
         'USER' : 'root',
         'PASSWORD' : 'activedev',
-        'HOST': '127.0.0.1',
+        'HOST': 'reducedev2',
         'PORT': '3306',
     }
 }

### 2017-07-14 autoreduce_webapp/reduction_variables/utils.py

@@ -7,6 +7,7 @@ from reduction_variables.models import InstrumentVariable, RunVariable
 from reduction_viewer.models import ReductionRun, Notification
 from reduction_viewer.utils import InstrumentUtils, StatusUtils, ReductionRunUtils
 from autoreduce_webapp.icat_cache import ICATCache
+from autoreduce_webapp.icat_communication import ICATCommunication
 
 class DataTooLong(ValueError):
     pass
@@ -205,7 +206,7 @@ class InstrumentVariablesUtils(object):
         
         # Get the upcoming experiments, and then select all variables for these experiments.
         upcoming_experiments = []
-        with ICATCache() as icat:
+        with ICATCommunication() as icat:
             upcoming_experiments = list(icat.get_upcoming_experiments_for_instrument(instrument_name))
         upcoming_variables_by_experiment = InstrumentVariable.objects.filter(instrument = instrument, experiment_reference__in = upcoming_experiments).order_by('experiment_reference')
                 

### 2017-07-14 autoreduce_webapp/reduction_viewer/utils.py

@@ -1,10 +1,12 @@
 import logging, os, sys, time, datetime
+
 sys.path.append(os.path.join("../", os.path.dirname(os.path.dirname(__file__))))
 os.environ["DJANGO_SETTINGS_MODULE"] = "autoreduce_webapp.settings"
 logger = logging.getLogger('app')
 from django.utils import timezone
 from reduction_viewer.models import Instrument, Status, ReductionRun, DataLocation
 from reduction_variables.models import RunVariable
+
 
 class StatusUtils(object):
     def _get_status(self, status_value):
@@ -30,7 +32,8 @@ class StatusUtils(object):
 
     def get_skipped(self):
         return self._get_status("Skipped")
-            
+
+
 class InstrumentUtils(object):
     def get_instrument(self, instrument_name):
         """
@@ -42,56 +45,55 @@ class InstrumentUtils(object):
             instrument.save()
             logger.warn("%s instrument was not found, created it." % instrument_name)
         return instrument
-        
-class ReductionRunUtils(object):
 
+
+class ReductionRunUtils(object):
     def cancelRun(self, reductionRun):
         """
         Try to cancel the run given, or the run that was scheduled as the next retry of the run. When we cancel, we send a message to the backend queue processor, telling it to ignore this run if it arrives (most likely through a delayed message through ActiveMQ's scheduler). We also set statuses and error messages. If we can't do any of the above, we set the variable (retry_run.cancel) that tells the frontend to not schedule another retry if the next run fails.
         """
         from reduction_variables.utils import MessagingUtils
-        
+
         def setCancelled(run):
             run.message = "Run cancelled by user"
             run.status = StatusUtils().get_error()
             run.finished = timezone.now().replace(microsecond=0)
             run.retry_when = None
             run.save()
-        
-        if reductionRun.status == StatusUtils().get_queued(): # this is the queued run, send the message to queueProcessor to cancel it
+
+        if reductionRun.status == StatusUtils().get_queued():  # this is the queued run, send the message to queueProcessor to cancel it
             MessagingUtils().send_cancel(reductionRun)
             setCancelled(reductionRun)
-            
+
         # otherwise this run has already failed, and we're looking at a scheduled rerun of it
-        elif not reductionRun.retry_run: # we don't actually have a rerun, so just ensure the retry time is set to "Never" (None)
+        elif not reductionRun.retry_run:  # we don't actually have a rerun, so just ensure the retry time is set to "Never" (None)
[…]

### 2017-07-14 autoreduce_webapp/autoreduce_webapp/templatetags/get_user_name.py
Caught an exception which could cause errors displaying user names on the development system

@@ -2,6 +2,9 @@ from django.template import Library, Node, Variable, \
     VariableDoesNotExist, TemplateSyntaxError
 from django.contrib.auth.models import User
 from django.utils.safestring import mark_safe
+from django.core.exceptions import ObjectDoesNotExist
+import logging
+logger = logging.getLogger(__name__)
 
 register = Library()
  
@@ -18,7 +21,10 @@ class UserNameNode(Node):
  
     def render(self, context):
         usernumber = unicode(get_var(self.usernumber, context))
-        person = User.objects.get(username=usernumber)
+        try:
+            person = User.objects.get(username=usernumber)
+        except ObjectDoesNotExist as e:
+            return mark_safe('Autoreduction Service')
         return mark_safe('<a href="mailto:' + person.email + '">'+ person.first_name + " " + person.last_name + '</a>')
  
 @register.tag

### 2018-07-16 QueueProcessors/QueueProcessor/queue_processor.py
Changed to please pylint

@@ -15,15 +15,14 @@ import sys
 import time
 import traceback
 
-import stomp
-
 from QueueProcessors.QueueProcessor.base import session
 from QueueProcessors.QueueProcessor.orm_mapping import (ReductionRun, Instrument,
                                                         Status, Experiment,
                                                         DataLocation, ReductionLocation)
 # pylint: disable=cyclic-import
 from QueueProcessors.QueueProcessor.queueproc_utils.messaging_utils import MessagingUtils
-from QueueProcessors.QueueProcessor.queueproc_utils.instrument_variable_utils import InstrumentVariablesUtils
+from QueueProcessors.QueueProcessor.queueproc_utils.instrument_variable_utils \
+    import InstrumentVariablesUtils
 from QueueProcessors.QueueProcessor.queueproc_utils.status_utils import StatusUtils
 from QueueProcessors.QueueProcessor.queueproc_utils.reduction_run_utils import ReductionRunUtils
 # pylint: disable=import-error, no-name-in-module
@@ -31,7 +30,6 @@ from QueueProcessors.QueueProcessor.settings import (LOGGING, EMAIL_HOST,
                                                      EMAIL_PORT, EMAIL_ERROR_RECIPIENTS,
                                                      EMAIL_ERROR_SENDER, BASE_URL)
 
-from utils.clients.icat_client import ICATClient
 from utils.clients.queue_client import QueueClient
 
 # Set up logging and attach the logging to the right part of the config.
@@ -421,7 +419,7 @@ class Listener(object):
         new_job = ReductionRunUtils().create_retry_run(reduction_run, delay=retry_in)
         try:
             #  Seconds to Milliseconds
-            MessagingUtils().send_pending(new_job, delay=retry_in * 1000)
+            MessagingUtils().send_pending(new_job)
         except Exception as exp:
             logger.error(traceback.format_exc())
             new_job.delete()  # pylint: disable=no-member
@@ -435,16 +433,16 @@ def setup_connection(consumer_name):
     activemq_client.connect()
 
     # Register the event listener
-    conn = activemq_client.get_connection()    
+    conn = activemq_client.get_connection()
     listener = Listener(activemq_client)
     conn.set_listener(consumer_name, listener)
     time.sleep(0.5)
 
     # Subscribe to the queues
     destinations = ['/queue/DataReady',
-        '/queue/ReductionStarted',
-        '/queue/ReductionComplete',
-        '/queue/ReductionError']
[…]

### 2018-07-16 QueueProcessors/QueueProcessor/queueproc_utils/messaging_utils.py

@@ -16,10 +16,10 @@ logger = logging.getLogger("queue_processor") # pylint: disable=invalid-name
 
 class MessagingUtils(object):
     """ Utils class for sending messages to queues. """
-    def send_pending(self, reduction_run, delay=None):
+    def send_pending(self, reduction_run):
         """ Sends a message to the queue with the details of the job to run. """
         data_dict = self._make_pending_msg(reduction_run)
-        self._send_pending_msg(data_dict, delay)
+        self._send_pending_msg(data_dict)
 
     def send_cancel(self, reduction_run):
         """ Sends a message to the queue telling it to cancel any reruns of the job. """
@@ -57,15 +57,12 @@ class MessagingUtils(object):
         return data_dict
 
     @staticmethod
-    def _send_pending_msg(data_dict, delay=None):
+    def _send_pending_msg(data_dict):
         """ Sends data_dict to ReductionPending (with the specified delay) """
         # To prevent circular dependencies
-        from ..queue_processor import Client as ActiveMQClient
-
         message_client = QueueClient()
         message_client.connect()
         message_client.send('/queue/ReductionPending',
                             json.dumps(data_dict),
-                            priority = '0',
-                            delay=delay)
+                            priority='0')
         message_client.stop()

### 2018-07-16 QueueProcessors/QueueProcessor/queueproc_utils/reduction_run_utils.py

@@ -9,7 +9,8 @@ from QueueProcessors.QueueProcessor.base import session
 from QueueProcessors.QueueProcessor.settings import LOGGING
 from QueueProcessors.QueueProcessor.orm_mapping import DataLocation, ReductionRun, RunJoin
 
-from QueueProcessors.QueueProcessor.queueproc_utils.instrument_variable_utils import InstrumentVariablesUtils
+from QueueProcessors.QueueProcessor.queueproc_utils.instrument_variable_utils \
+    import InstrumentVariablesUtils
 from QueueProcessors.QueueProcessor.queueproc_utils.messaging_utils import MessagingUtils
 from QueueProcessors.QueueProcessor.queueproc_utils.status_utils import StatusUtils
 from QueueProcessors.QueueProcessor.queueproc_utils.variable_utils import VariableUtils

### 2018-07-16 QueueProcessors/QueueProcessor/queue_processor.py
Added delay to queue_client.py send method

@@ -419,7 +419,7 @@ class Listener(object):
         new_job = ReductionRunUtils().create_retry_run(reduction_run, delay=retry_in)
         try:
             #  Seconds to Milliseconds
-            MessagingUtils().send_pending(new_job)
+            MessagingUtils().send_pending(new_job, delay=retry_in * 1000)
         except Exception as exp:
             logger.error(traceback.format_exc())
             new_job.delete()  # pylint: disable=no-member

### 2018-07-16 QueueProcessors/QueueProcessor/queueproc_utils/messaging_utils.py

@@ -16,10 +16,10 @@ logger = logging.getLogger("queue_processor") # pylint: disable=invalid-name
 
 class MessagingUtils(object):
     """ Utils class for sending messages to queues. """
-    def send_pending(self, reduction_run):
+    def send_pending(self, reduction_run, delay=None):
         """ Sends a message to the queue with the details of the job to run. """
         data_dict = self._make_pending_msg(reduction_run)
-        self._send_pending_msg(data_dict)
+        self._send_pending_msg(data_dict, delay)
 
     def send_cancel(self, reduction_run):
         """ Sends a message to the queue telling it to cancel any reruns of the job. """
@@ -57,12 +57,13 @@ class MessagingUtils(object):
         return data_dict
 
     @staticmethod
-    def _send_pending_msg(data_dict):
+    def _send_pending_msg(data_dict, delay=None):
         """ Sends data_dict to ReductionPending (with the specified delay) """
         # To prevent circular dependencies
         message_client = QueueClient()
         message_client.connect()
         message_client.send('/queue/ReductionPending',
                             json.dumps(data_dict),
-                            priority='0')
+                            priority='0',
+                            delay=delay)
         message_client.stop()

### 2018-07-17 Documentation/paper/paper.tex

@@
 \title{\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}}
-\author{J. R. Corderoy, T. Gowland, L. Greenwood, M. Noble, D. Oram and A. J. Markvardsen \\
+\author{J. R. Corderoy, T. Gowland, L. Greenwood, M. Noble, D. Oram, \\
+	A. J. Markvardsen, J. Shears, E. Oram, D. Fairbrother and G. Christian \\
 (code contributors)\\
@@
 
-\subsection{Reduction scripts}\label{reduction-scripts}
+\subsection{Reduction Scripts}\label{reduction-scripts}
 
@@
 
-\subsection{Web app}\label{web-app}
+\subsection{WebApp}\label{web-app}
 
@@
 
+\begin{figure*}
+	\centering\includegraphics[width=0.8\linewidth]{machine_layout.png}
+	\caption{An image showing which services are installed on which machines}
+	\label{fig:machine_layout}
+\end{figure*}
+
 \section{Deployment}\label{deployment}
@@
 
-There is then a second node which runs Red Hat Enterprise Linux 7\cite{rhel}. This node
+There is then a second node which runs Windows Server 2012 running on the same Hyper-V cluster. This node
 manages the parts of the system which are common between front and backend. This includes:
@@
 
-The third and final node manages the parts of the system that could be replicated such that 
+The third and final node, running Red Hat Enterprise Linux 7\cite{rhel}, manages the parts of the system that could be replicated such that 
 we can have multiple worker nodes active in order to split the load of autoreduction and speed
@@
 
+A diagram of the different parts of the system is shown in figure \ref{fig:machine_layout}
+
 The system is split out in this way such that if the machine with the WebApp installed were to fail,
@@
 
-The software written as part this project is not tied to a
-particular operating system since it is written entirely in Python and Django.
+The software written as part this project is not tied to a particular operating system since 
+it is written entirely in Python. However there is one limitation, the EndOfRunMonitor
+cannot be ran on Linux as a network mounted drive does not produce the required filesytem events.
 
@@
   easier deployment
+
 \end{enumerate}
@@
 processing data as soon as it comes off beamlines rather then waiting for files 
-to be written to disk.
+to be written to disk. Also an API could be implemented to reduce the complexity of
+the QueueProcessor and allow integration of autoreduction into other software \cite{autoreduction-api}.
 
@@
 
-\bibitem{Docker}
+\bibitem{docker}
 	Docker,
@@
 	\url{https://www.docker.com/}
-
-\bibitem{iis}
-    Microsoft Corporation,
-    \emph{IIS},
-    \url{http://www.iis.net/}.
-
-\bibitem{fcgi}
-    \emph{FastCGI},
-    \url{https://github.com/FastCGI-Archives/FastCGI.com}.
 
@@
 \bibitem{source}
-    \emph{Autoreduction repository},
-    \url{https://github.com/mantidproject/autoreduce}.
+    Autoreduction repository,
+    \url{https://github.com/isisScientificComputing/autoreduce}.
+
+\bibitem{autoreduction-api}
+  Autoreduction API GitHub issue
+  \url{https://github.com/ISISScientificComputing/autoreduce/issues/73}.
 

### 2018-07-17 QueueProcessors/QueueProcessor/queue_processor.py
Put queue subscription into the QueueClient class and removed sleep

@@ -435,17 +435,11 @@ def setup_connection(consumer_name):
     # Register the event listener
     conn = activemq_client.get_connection()
     listener = Listener(activemq_client)
-    conn.set_listener(consumer_name, listener)
-    time.sleep(0.5)
-
-    # Subscribe to the queues
     destinations = ['/queue/DataReady',
                     '/queue/ReductionStarted',
                     '/queue/ReductionComplete',
                     '/queue/ReductionError']
-    for dest in destinations:
-        logger.info("Subscribing to %s", dest)
-        conn.subscribe(destination=dest, id=1, ack='auto')
+    activemq_client.subscribe_queues(consumer_name, listener, destinations)
 
 def main():
     """ Main method. """

### 2018-07-17 utils/clients/queue_client.py

@@ -86,6 +86,16 @@ class QueueClient(object):
             self._connection.stop()
         self._connection = None
 
+    def subscribe_queues(consumer_name, listener, destinations):
+        """
+        Subscribe the listener to the specified destinations.
+        """
+        self._connection.set_listener(listener)
+        for dest in destinations:
+            logging.info("Subscribing to %s", dest)
+            self._connection.subscribe(destination=dest, id=1, ack='auto')
+        
+
     def send(self, destination, message, persistent='true', priority='4', delay=None):
         """
         Send a message via the open connection to a queue

### 2018-07-17 QueueProcessors/QueueProcessor/queue_processor.py
Reverted to e81b954 and removed sleep

@@ -12,7 +12,6 @@ import json
 import logging.config
 import smtplib
 import sys
-import time
 import traceback
 
 from QueueProcessors.QueueProcessor.base import session
@@ -435,11 +434,16 @@ def setup_connection(consumer_name):
     # Register the event listener
     conn = activemq_client.get_connection()
     listener = Listener(activemq_client)
+    conn.set_listener(consumer_name, listener)
+
+    # Subscribe to the queues
     destinations = ['/queue/DataReady',
                     '/queue/ReductionStarted',
                     '/queue/ReductionComplete',
                     '/queue/ReductionError']
-    activemq_client.subscribe_queues(consumer_name, listener, destinations)
+    for dest in destinations:
+        logger.info("Subscribing to %s", dest)
+        conn.subscribe(destination=dest, id=1, ack='auto')
 
 def main():
     """ Main method. """

### 2018-07-17 utils/clients/queue_client.py

@@ -86,16 +86,6 @@ class QueueClient(object):
             self._connection.stop()
         self._connection = None
 
-    def subscribe_queues(consumer_name, listener, destinations):
-        """
-        Subscribe the listener to the specified destinations.
-        """
-        self._connection.set_listener(listener)
-        for dest in destinations:
-            logging.info("Subscribing to %s", dest)
-            self._connection.subscribe(destination=dest, id=1, ack='auto')
-        
-
     def send(self, destination, message, persistent='true', priority='4', delay=None):
         """
         Send a message via the open connection to a queue

### 2018-07-17 build/commands/database.py
Reapply folder re-org following master merge

@@ -1,0 +1,44 @@
+"""
+Module to generate a testing database to be used for local testing of the project
+"""
+import os
+# pylint:disable=no-name-in-module,import-error
+from distutils.core import Command
+
+from build.database.generate_database import run_sql_file, generate_schema
+from build.utils.common import BUILD_LOGGER, ROOT_DIR
+
+
+class InitialiseTestDatabase(Command):
+    """
+    Command to initialise the local host database and populate it with dummy data
+    """
+    description = 'Create the test database on local host'
+    user_options = []
+
+    def initialize_options(self):
+        """ Initialise path variables """
+        # pylint:disable=attribute-defined-outside-init
+        self.setup_sql_path = None
+        self.populate_sql_path = None
+
+    def finalize_options(self):
+        """ Generate paths to sql scripts """
+        database_build_dir = os.path.join(ROOT_DIR, 'build', 'database')
+        # pylint:disable=attribute-defined-outside-init
+        self.setup_sql_path = os.path.join(database_build_dir, 'test_db_setup.sql')
+        self.populate_sql_path = os.path.join(database_build_dir, 'populate_reduction_viewer.sql')
+
+    def run(self):
+        """ Run the setup scripts required for localhost database """
+        BUILD_LOGGER.print_and_log("==================== Building Database ======================")
+        BUILD_LOGGER.print_and_log("Setting up database on local host")
+        if run_sql_file(self.setup_sql_path, BUILD_LOGGER.logger) is False:
+            return
+        BUILD_LOGGER.print_and_log("Migrating databases from django model")
+        if generate_schema(ROOT_DIR, BUILD_LOGGER.logger) is False:
+            return
+        BUILD_LOGGER.print_and_log("Populating database with test data")
+        if run_sql_file(self.populate_sql_path, BUILD_LOGGER.logger) is False:
+            return
+        BUILD_LOGGER.print_and_log("Test database successfully initialised\n")

### 2018-07-17 build/commands/help.py

@@ -1,0 +1,47 @@
+"""
+Command to print the help information for setup.py
+"""
+from __future__ import print_function
+
+# pylint:disable=no-name-in-module,import-error
+from distutils.core import Command
+
+
+class Help(Command):
+    """
+    Command class to display help message
+    """
+
+    description = "Provide help on using this setup"
+    user_options = []
+
+    def initialize_options(self):
+        """ No args hence pass """
+        pass
+
+    def finalize_options(self):
+        """ No args hence pass """
+        pass
+
+    # pylint:disable=no-self-use
+    def run(self):
+        """
+        Print out the help documentation to console
+        """
+        help_text = (('Usage       :', 'python setup.py [commands]'),
+                     ('Description :', 'Script to setup project and testing environment'),
+                     ('', ''),
+                     ('Commands: ', '')
+                    )
+        commands = (('     test_settings', 'Copy test_settings.py to settings.py'),
+                    ('     database', 'Initialise database on localhost'),
+                    ('     externals', 'Install all external programs'),
+                    ('              ', 'Use the -s argument to specify a comma separated list of services:'),
+                    ('              ', '    python setup.py -s activemq,icat,mantid'),
+                    ('     start', 'starts required services: activemq'),
+                    ('     help', 'Show the help documentation')
+                   )
+        for args in help_text:
+            print('{0:<15} {1:<10}'.format(*args))
+        for command in commands:
+            print('{0:<20} {1:<10}'.format(*command))

### 2018-07-17 build/commands/start.py

@@ -1,0 +1,60 @@
+"""
+Command to start services running
+"""
+from __future__ import print_function
+
+import os
+import time
+
+# pylint:disable=no-name-in-module,import-error
+from distutils.core import Command
+
+from build.utils.process_runner import run_process_and_log, run_process_with_shell
+
+
+class Start(Command):
+    """
+    Command to start the activeMQ service
+    """
+
+    description = 'Start the services that are required to test the project: ActiveMQ'
+    user_options = []
+
+    def initialize_options(self):
+        """ Currently not required as we are only starting ActiveMQ
+            If more services become required we will need to add parameters for this"""
+        pass
+
+    def finalize_options(self):
+        """ See above comment regarding only ActiveMQ """
+        pass
+
+    # pylint:disable=no-self-use
+    def run(self):
+        """
+        If activemq in expected install path, run `activemq start`
+        """
+        from build.settings import INSTALL_DIRS
+        location = os.path.join(INSTALL_DIRS['activemq'],
+                           'apache-activemq-5.15.3',
+                           'bin')
+        if os.name == 'nt':
+            location = os.path.join(location, 'activemq.bat')
+            start_new_terminal = ['start', 'cmd', '/c']
+            if self._check_valid_path(location):
+                run_process_with_shell(start_new_terminal + [location, 'start'])
+                time.sleep(2)  # Ensure that activemq process has started before you continue
+        else:
+            location = os.path.join(location, 'activemq')
+            if self._check_valid_path(location):
+                run_process_and_log([location, 'start'])
+                time.sleep(2)  # Ensure that activemq process has started before you continue
+
+    @staticmethod
+    def _check_valid_path(path):
+        if os.path.isfile(path):
+                return True
+        else:
+            print("Unable to start ActiveMQ service."
+                  "Files not found at location %s" % path)
+            return False

### 2018-07-17 build/database/generate_database.py

@@ -1,0 +1,70 @@
+"""
+Python wraps to windows/linux schema generation scripts for services
+"""
+from __future__ import print_function
+
+import os
+import subprocess
+import sys
+
+from build.utils.process_runner import run_process_and_log
+
+PATH_TO_DIR = os.path.dirname(os.path.realpath(__file__))
+
+
+def run_sql_file(sql_file_location, logger):
+    """
+    Runs a sql file on the localhost database
+    :param sql_file_location: file path to the sql file
+    :param logger: log handler
+    :return: True: exit code of script was 0
+             False: exit code of script was non-zero
+    """
+    from build.settings import DB_ROOT_PASSWORD
+    logger.info("Running script: %s" % sql_file_location)
+    with open(sql_file_location, 'r') as input_file:
+        password = ''
+        if DB_ROOT_PASSWORD:
+            password = 'MYSQL_PWD=%s ' % DB_ROOT_PASSWORD
+        access_string = "mysql -u{0} {1}".format('root', password)
+        mysql_process = subprocess.Popen(access_string,
+                                         stdin=input_file, shell=True,
+                                         stdout=subprocess.PIPE,
+                                         stderr=subprocess.PIPE)
+        process_output, process_err = mysql_process.communicate()
+        if process_output != '':
+            logger.info(process_output)
+        if process_err != '':
+            logger.error(process_err)
+            print("Script did not complete. Check build.log for more details.")
+            print(process_err, file=sys.stderr)
+            return False
+    logger.info("Script ran successfully")
+    return True
+
+
+def generate_schema(project_root_path, logger):
+    """
+    Call django migrations to create testing database schema
+    :param project_root_path: The full path to the root directory of the project
+    :param logger: log handler
+    :return: True: exit code of script was 0
+             False: exit code of script was non-zero
+    """
+    path_to_manage = os.path.join(project_root_path, 'WebApp', 'autoreduce_webapp', 'manage.py')
+    for database in ['admin', 'sessions', 'auth', 'reduction_viewer', 'reduction_variables']:
+        logger.info("Migrating %s" % database)
+        if run_process_and_log(['python', path_to_manage, 'makemigrations', database]) is False:
+            logger.error("Error encountered when makingmigrations for %s" % database)
+            return False
+        if run_process_and_log(['python', path_to_manage, 'migrate', database]) is False:
+            logger.error("Error encountered when migrating %s" % database)
+            return False
+
+    logger.info("Adding super user")
[…]

### 2018-07-17 build/install/activemq.sh

@@ -1,0 +1,10 @@
+#!/bin/sh
+
+set -e
+
+sudo mkdir -p $1
+
+echo "Downloading ActiveMQ"
+sudo wget -O $1/activemq.tar.gz "http://www.apache.org/dyn/closer.cgi?filename=/activemq/5.15.3/apache-activemq-5.15.3-bin.tar.gz&action=download" -q
+sudo tar xvf $1/activemq.tar.gz -C $1
+sudo chmod 755 $1/apache-activemq-5.15.3/bin/activemq

### 2018-07-17 build/install/install_services.py

@@ -1,0 +1,72 @@
+"""
+Python wraps to windows/linux install scripts for services
+"""
+import logging
+import os
+
+from build.settings import INSTALL_DIRS
+from build.utils.process_runner import run_process_and_log
+
+PATH_TO_DIR = os.path.dirname(os.path.realpath(__file__))
+
+
+def valid_services():
+    """
+    :return: A list of all valid services for the operating system
+    """
+    valid = ['icat', 'activemq']
+    if os.name == 'nt':
+        valid.append('mantid')
+        valid.append('7zip')
+    else:
+        valid.append('mantid')
+    return valid
+
+
+def validate_input(list_of_services, logger):
+    """
+    Ensure that all the service names provided by the user are valid
+    :param list_of_services: List of user provided services
+    :param logger: Handle to the Build logger
+    :return: True: All services are valid
+             False: Will print and log invalid service(s)
+    """
+    valid_services_list = valid_services()
+    all_services_valid = True
+    for service in list_of_services:
+        if service.lower() not in valid_services_list:
+            logger.print_and_log("\"%s\" not recognised as a valid service "
+                                 "for this operating system." % service, logging.ERROR)
+            all_services_valid = False
+    return all_services_valid
+
+
+def install_service(service_name, log_handler):
+    """
+    Given a service name, find the correct install script, run it and return boolean for success
+    :param service_name: The name of the service to install
+    :param log_handler: Handler for logging build info
+    :return: True: exit code of installation script was 0
+             False: exit code of installation script was non-zero
+    """
+    install_script = os.path.join(PATH_TO_DIR, (service_name + '.{}'))
+    install_path = INSTALL_DIRS[service_name]
+    unzip_path = ''
+    if os.name == 'nt':
+        if service_name == 'mantid':
+            # No need to install mantid on windows currently so skip this
+            return True
+        install_script = install_script.format('bat')
+        unzip_path = INSTALL_DIRS['7zip-location']
+    else:
+        install_script = install_script.format('sh')
+
+    log_handler.logger.info("Installing %s with script %s" % (service_name, install_script))
+    if run_process_and_log([install_script, install_path, unzip_path]) is False:
+        log_handler.print_and_log("Error encountered when installing %s. "
+                                  "Check the build.log for more information." % service_name,
+                                  logging.ERROR)
+        return False
+
+    log_handler.print_and_log("%s installed successfully" % service_name)
+    return True

### 2018-07-17 build/install/mantid.sh

@@ -1,0 +1,11 @@
+#!/bin/sh
+
+set -e
+
+# Add GPG key and upstream Mantid repo
+sudo apt-add-repository "deb [arch=amd64] http://apt.isis.rl.ac.uk $(lsb_release -c | cut -f 2) main" -y
+# add the signing key
+wget -O - http://apt.isis.rl.ac.uk/2E10C193726B7213.asc -q | sudo apt-key add -
+sudo apt-add-repository ppa:mantid/mantid -y
+
+sudo apt-get install mantid

### 2018-07-17 build/test_settings.py

@@ -1,0 +1,25 @@
+# pylint: skip-file
+"""
+Settings for install directories
+"""
+import os
+
+if os.name == 'nt':
+    # WINDOWS SETTINGS
+    INSTALL_DIRS = {
+        'activemq': 'C:\\autoreduction_deps\\activemq\\',
+        'icat': 'C:\\autoreduction_deps\\icat\\',
+        'mantid': 'C:\\autoreduction_deps\\mantid\\',
+        '7zip': 'C:\\autoreduction_deps\\7zip\\',
+        '7zip-location': 'C:\\Program Files\\7-Zip',  # Expected install location of 7Zip
+    }
+else:
+    # LINUX SETTINGS
+    INSTALL_DIRS = {
+        'activemq': '/opt/autoreduce_deps/activemq',
+        'icat': '/opt/autoreduce_deps/icat',
+        'mantid': '/opt/Mantid'
+    }
+    # 7Zip not required on linux
+
+DB_ROOT_PASSWORD = ''

### 2018-07-17 build/tests/test_pylint.sh

@@ -1,0 +1,40 @@
+#!/bin/sh
+# Run pylint without check for C0103 (invalid-name) as this triggers on module names
+# There is currently no work around for this - we should change module names to lower case
+
+SUCCESS=0
+FILES="build
+       EndOfRunMonitor
+       Scripts/ActiveMQTests/send_message.py
+       Scripts/ActiveMQTests/test_stomp_activemq.py
+       Scripts/ManualSubmissionScript
+       Scripts/NagiosChecks/autoreduce_checklastrun.py
+       WebApp/autoreduce_webapp/autoreduce_webapp/
+       QueueProcessors/AutoreductionProcessor
+      "
+
+for file in $FILES
+do
+    RESULT="$(pylint -d C0103 $file)"
+    retVal=$?
+    if [ $retVal -ne 0 ]; then
+        echo "$RESULT"
+        SUCCESS=1
+    fi
+done
+
+
+# Should be able to improve the below when we fix W0141,R0401
+
+RESULT="$(pylint -d C0103,W0141,R0401 QueueProcessors/QueueProcessor)"
+retVal=$?
+if [ $retVal -ne 0 ]; then
+    echo "$RESULT"
+    SUCCESS=1
+fi
+
+if [ $SUCCESS -ne 0 ]; then
+    exit 1
+else
+    exit 0
+fi

### 2018-07-17 build/utils/process_runner.py

@@ -1,0 +1,34 @@
+"""
+Wrapper for running subprocesses
+"""
+
+import subprocess
+
+from build.utils.common import BUILD_LOGGER
+
+
+def run_process_and_log(list_of_args):
+    """
+    Call a process using Popen and logs output to file
+    :param list_of_args: list of arguments for Popen
+    """
+    process = subprocess.Popen(list_of_args,
+                               stdout=subprocess.PIPE,
+                               stderr=subprocess.PIPE)
+    process_output, process_error = process.communicate()
+    exit_status = process.returncode
+    if process_output:
+        BUILD_LOGGER.logger.info(process_output)
+    if exit_status != 0:
+        BUILD_LOGGER.logger.error(process_error)
+        return False
+    return True
+
+
+def run_process_with_shell(list_of_args):
+    """
+    Run a process using the shell true command and do not log the output
+    :param list_of_args: list of args for Popen
+    :return:
+    """
+    subprocess.call(list_of_args, shell=True)

### 2018-07-17 build/commands/database.py
Ensure test-user is added in DB migration

@@ -5,7 +5,7 @@ import os
 # pylint:disable=no-name-in-module,import-error
 from distutils.core import Command
 
-from build.database.generate_database import run_sql_file, generate_schema
+from build.database.generate_database import add_test_user, run_sql_file, generate_schema
 from build.utils.common import BUILD_LOGGER, ROOT_DIR
 
 
@@ -40,5 +40,8 @@ class InitialiseTestDatabase(Command):
             return
         BUILD_LOGGER.print_and_log("Populating database with test data")
         if run_sql_file(self.populate_sql_path, BUILD_LOGGER.logger) is False:
+            return
+        BUILD_LOGGER.print_and_log("Adding test user from settings")
+        if add_test_user(BUILD_LOGGER.logger) is False:
             return
         BUILD_LOGGER.print_and_log("Test database successfully initialised\n")

### 2018-07-17 build/database/generate_database.py

@@ -7,6 +7,9 @@ import os
 import subprocess
 import sys
 
+from build.settings import DB_ROOT_PASSWORD
+from utils.settings import MYSQL
+
 from build.utils.process_runner import run_process_and_log
 
 PATH_TO_DIR = os.path.dirname(os.path.realpath(__file__))
@@ -20,7 +23,7 @@ def run_sql_file(sql_file_location, logger):
     :return: True: exit code of script was 0
              False: exit code of script was non-zero
     """
-    from build.settings import DB_ROOT_PASSWORD
+
     logger.info("Running script: %s" % sql_file_location)
     with open(sql_file_location, 'r') as input_file:
         password = ''
@@ -39,7 +42,7 @@ def run_sql_file(sql_file_location, logger):
             print("Script did not complete. Check build.log for more details.")
             print(process_err, file=sys.stderr)
             return False
-    logger.info("Script ran successfully")
+    logger.info("Script completed successfully")
     return True
 
 
@@ -67,4 +70,31 @@ def generate_schema(project_root_path, logger):
         logger.error("Error encountered when adding super user")
         return False
     logger.info("Database migrated successfully")
+    return True
+
+def add_test_user(logger):
+    user_to_add = MYSQL["USER"]
+    logger.info("Adding user: {0}".format(user_to_add))
+    sql_commands = ["GRANT ALL ON *.* TO '{0}'@'localhost' IDENTIFIED BY '{1}';".format(user_to_add, MYSQL["PASSWD"]),
+                    "FLUSH PRIVILEGES;"]
+
+    to_exec = '\n'.join(sql_commands)
+
+    # This is duplicated from above, ideally we should switch to using Python-MySQL connectors
+    password = ''
+    if DB_ROOT_PASSWORD:
+        password = 'MYSQL_PWD=%s ' % DB_ROOT_PASSWORD
+    access_string = "mysql -u{0} {1}".format('root', password)
+    mysql_process = subprocess.Popen(access_string,
+                                     stdin=subprocess.PIPE, shell=True,
+                                     stdout=subprocess.PIPE,
+                                     stderr=subprocess.PIPE)
+    process_output, process_err = mysql_process.communicate(input=to_exec)
+    if process_output != '':
+        logger.info(process_output)
+    if process_err != '':
+        logger.error(process_err)
+        print("Script did not complete. Check build.log for more details.")
+        print(process_err, file=sys.stderr)
+        return False
     return True

### 2018-07-17 scripts/manual_submission_script/manual_submission.py

@@ -7,13 +7,6 @@ import json
 import sys
 import argparse
 
-<<<<<<< HEAD:Scripts/ManualSubmissionScript/manual_submission.py
-import icat
-import stomp
-
-
-=======
->>>>>>> origin/develop:scripts/manual_submission_script/manual_submission.py
 # The below is only a template on the repo
 # pylint: disable=import-error, no-name-in-module
 from utils.clients.icat_client import ICATClient

### 2018-07-17 build/database/generate_database.py
Move DB password import into function

@@ -7,9 +7,6 @@ import os
 import subprocess
 import sys
 
-from build.settings import DB_ROOT_PASSWORD
-from utils.settings import MYSQL
-
 from build.utils.process_runner import run_process_and_log
 
 PATH_TO_DIR = os.path.dirname(os.path.realpath(__file__))
@@ -23,7 +20,7 @@ def run_sql_file(sql_file_location, logger):
     :return: True: exit code of script was 0
              False: exit code of script was non-zero
     """
-
+    from build.settings import DB_ROOT_PASSWORD  # Must be imported at run-time for migrate test settings to work
     logger.info("Running script: %s" % sql_file_location)
     with open(sql_file_location, 'r') as input_file:
         password = ''
@@ -73,6 +70,9 @@ def generate_schema(project_root_path, logger):
     return True
 
 def add_test_user(logger):
+    # Must be imported at run-time for migrate test settings to work
+    from build.settings import DB_ROOT_PASSWORD
+    from utils.settings import MYSQL
     user_to_add = MYSQL["USER"]
     logger.info("Adding user: {0}".format(user_to_add))
     sql_commands = ["GRANT ALL ON *.* TO '{0}'@'localhost' IDENTIFIED BY '{1}';".format(user_to_add, MYSQL["PASSWD"]),
@@ -81,9 +81,7 @@ def add_test_user(logger):
     to_exec = '\n'.join(sql_commands)
 
     # This is duplicated from above, ideally we should switch to using Python-MySQL connectors
-    password = ''
-    if DB_ROOT_PASSWORD:
-        password = 'MYSQL_PWD=%s ' % DB_ROOT_PASSWORD
+    password = '' if not DB_ROOT_PASSWORD else 'MYSQL_PWD=%s ' % DB_ROOT_PASSWORD
     access_string = "mysql -u{0} {1}".format('root', password)
     mysql_process = subprocess.Popen(access_string,
                                      stdin=subprocess.PIPE, shell=True,

### 2018-07-17 utils/clients/database_client.py
Print connect string to debug travis build

@@ -47,6 +47,7 @@ class DatabaseClient(object):
                                                               self._password,
                                                               self._host,
                                                               self._database_name)
+            print(connect_string)
             self._engine = create_engine(connect_string, pool_recycle=280)
             self._meta_data = MetaData(self._engine)
             session = sessionmaker(bind=self._engine)

### 2018-07-17 build/install/install_services.py
Fix CRLF ending in mantid.sh

@@ -14,12 +14,9 @@ def valid_services():
     """
     :return: A list of all valid services for the operating system
     """
-    valid = ['icat', 'activemq']
+    valid = ['icat', 'activemq', 'mantid']
     if os.name == 'nt':
-        valid.append('mantid')
         valid.append('7zip')
-    else:
-        valid.append('mantid')
     return valid
 
 

### 2018-07-18 build/install/mantid.sh
Check for sudo in ext install scripts

@@ -1,5 +1,13 @@
 #!/bin/sh
 
+# Test sudo
+$(sudo -n echo)
+exitCode=$?
+if [ $exitCode -ne 0 ] ; then
+    echo "This script must be run with sudo" >&2
+    exit 1
+fi
+
 set -e
 
 # Add GPG key and upstream Mantid repo
@@ -8,4 +16,4 @@ sudo apt-add-repository "deb [arch=amd64] http://apt.isis.rl.ac.uk $(lsb_release
 wget -O - http://apt.isis.rl.ac.uk/2E10C193726B7213.asc -q | sudo apt-key add -
 sudo apt-add-repository ppa:mantid/mantid -y
 
-sudo apt-get install mantid
+sudo apt-get install mantid -y

### 2018-07-19 Scripts/Build/tests/test_pylint.sh
updates to tests =and travis build
Refs #11

@@ -1,0 +1,38 @@
+#!/usr/bin/env sh
+# Run pylint without check for C0103 (invalid-name) as this triggers on module names
+# There is currently no work around for this - we should change module names to lower case
+
+SUCCESS=0
+FILES="monitors
+       scripts/ActiveMQTests/send_message.py
+       scripts/ActiveMQTests/test_stomp_activemq.py
+       scripts/manual_submission_script
+       scripts/NagiosChecks/autoreduce_checklastrun.py
+       WebApp/autoreduce_webapp/autoreduce_webapp/
+       QueueProcessors/AutoreductionProcessor"
+
+for file in $FILES
+do
+    RESULT="$(pylint -d C0103 $file)"
+    retVal=$?
+    if [ $retVal -ne 0 ]; then
+        echo "$RESULT"
+        SUCCESS=1
+    fi
+done
+
+
+# Should be able to improve the below when we fix W0141,R0401
+
+RESULT="$(pylint -d C0103,W0141,R0401 QueueProcessors/QueueProcessor)"
+retVal=$?
+if [ $retVal -ne 0 ]; then
+    echo "$RESULT"
+    SUCCESS=1
+fi
+
+if [ $SUCCESS -ne 0 ]; then
+    exit 1
+else
+    exit 0
+fi

### 2018-07-19 utils/clients/database_client.py

@@ -51,6 +51,7 @@ class DatabaseClient(object):
         return self._connection
 
     def _test_connection(self):
+        self._connection.execute('SELECT 1').fetchall()
         try:
             self._connection.execute('SELECT 1').fetchall()
         except Exception as exp:

### 2018-07-19 utils/clients/database_client.py
Fix pylint script permissions and remove testing statement
Refs #11

@@ -51,7 +51,6 @@ class DatabaseClient(object):
         return self._connection
 
     def _test_connection(self):
-        self._connection.execute('SELECT 1').fetchall()
         try:
             self._connection.execute('SELECT 1').fetchall()
         except Exception as exp:

### 2018-07-20 monitors/archive_monitor/isis_archive_monitor_win_service.py
Ensure windows services can be installed
Refs #11

@@ -3,14 +3,16 @@ Holds the class for overidding QueueService framework
 """
 # Can't import on travis (linux) server
 # pylint:disable=import-error
+import sys
 import servicemanager
 import win32event
+import win32serviceutil
 
 from monitors.windows_service import WindowsService
 from monitors.archive_monitor import isis_archive_monitor
 
 
-class QueueService(WindowsService):
+class PollService(WindowsService):
     """
     Class to override windows ServiceFramework
     """
@@ -36,3 +38,12 @@ class QueueService(WindowsService):
                 # Stop signal encountered
                 servicemanager.LogInfoMsg(self._svc_name_ + " - STOPPED")
                 break
+
+
+if __name__ == '__main__':
+    if len(sys.argv) == 1:
+        servicemanager.Initialize()
+        servicemanager.PrepareToHostSingle(PollService)
+        servicemanager.StartServiceCtrlDispatcher()
+    else:
+        win32serviceutil.HandleCommandLine(PollService)

### 2018-07-20 monitors/end_of_run_monitor/isis_monitor_win_service.py

@@ -8,14 +8,16 @@ difficulties whne watching for file changes.
 """
 # Can't import on travis (linux) server
 # pylint:disable=import-error
+import sys
 import servicemanager
 import win32event
+import win32serviceutil
 
 from monitors.end_of_run_monitor import isis_end_of_run_monitor
 from monitors.windows_service import WindowsService
 
 
-class QueueService(WindowsService):
+class MonitorService(WindowsService):
     """
     Class to override windows ServiceFramework
     """
@@ -42,3 +44,12 @@ class QueueService(WindowsService):
                 servicemanager.LogInfoMsg(self._svc_name_ + " - STOPPED")
                 isis_end_of_run_monitor.stop()
                 break
+
+
+if __name__ == '__main__':
+    if len(sys.argv) == 1:
+        servicemanager.Initialize()
+        servicemanager.PrepareToHostSingle(MonitorService)
+        servicemanager.StartServiceCtrlDispatcher()
+    else:
+        win32serviceutil.HandleCommandLine(MonitorService)
